### 2015-06-08 draft1.tex
Initial Commit

\documentclass[man]{apa}
\title{Sample Title}
\author{Murat Ambarkutuk}
\affiliation{English Language Institute, University of Delaware}
\note{6/8/2015; murata@udel.edu}
\abstract{Text of the abstract}

\acknowledgements{Thanks to people and grants, and your new address maybe.}

\shorttitle{Short Title as per APA manual}
\rightheader{Odd-Numbered Page Header}
\leftheader{Even-Numbered Page Header}
\begin{document}

trial
\end{document}

### 2015-06-08 draft1.tex
GRAD6 Version

@@
-\documentclass[man]{apa}
-\title{Sample Title}
+\documentclass[man]{apa6}
+\title{Sample Title} %Change Title
 \author{Murat Ambarkutuk}
-\affiliation{English Language Institute, University of Delaware}
-\note{6/8/2015; murata@udel.edu}
-\abstract{Text of the abstract}
-
-\acknowledgements{Thanks to people and grants, and your new address maybe.}
-
-\shorttitle{Short Title as per APA manual}
-\rightheader{Odd-Numbered Page Header}
-\leftheader{Even-Numbered Page Header}
+\affiliation{English Language Institute, University of Delaware \\ murata@udel.edu}
+\note{First Draft; 6/8/2015}
+\usepackage{apacite}
+\abstract{Of all the tools and methods invented by human kind to tame nature and make use of its challenges, the computer has had the greatest impact on society.
+Coupled with the Internet, computers have changed the way billions of humans work, entertain themselves, and think.
+Since the rise of the computers, Artificial Intelligence (AI) has been one of the most debated issues in the field of engineering.
+Research toward the creation of AI includes creation of self-aware machines that have superior intellectual abilities to that of human abilities.
+However, many researchers argue that the creation of AI will deeply change the society and will help human kind to solve major societal problems, while others refute the arguments for the conceptual invention because of ethical problems that AI will bring such as an anticipated human annihilation by these agents.
+This paper focuses on the the ethical problems that the creation of AI will raise.}
+\keywords{artificial intelligence, robotics, ethics, society} 
+\shorttitle{Short Title as per APA manual} %Change it
+\leftheader{Even-Numbered Page Header} %Change it
 \begin{document}
-
-trial
+\maketitle
+\section{Introduction}
+Although AI is a research topic in the fields of engineering and science, the first introduction of it was fictional literary and futuristic artistic works.
+For that reason, its popularity significantly
+ascended which resulted in becoming perhaps the most debated technology related term in the last century.
+Despite AI's popularity, it may be the most misunderstood term that in the field of engineering.
+In order to make clear its obfuscated definition, the tasks of AI should be mentioned.
+The task of AI is to create methods to enable machines to obtain symbolic data sets and manipulate them in order to solve generic problems in the most energy efficient and fastest fashion.
+The theory suggests that it is possible to achieve by imitating the processes of logical reasoning and decision making.
+Consequently, cognitive and perceptual systems of the human body have been scrutinized by researchers in order to emulate these processes at the hardware and software level.\par
+One common definition of AI is cited by Bostrom (n.d.), “A super-intelligence is any intellect that is vastly outperforms the best human brains in practically every field, including scientific creativity, general wisdom and social skills.” This definition clearly distinguishes specific domain intelligent agents and AI.
+Based on this definition a computer system, Deep Blue, which is a well-known computer system for its success in chess can be considered smart within a narrow domain rather than a genuine AI supported by limitations that Duffy (2006, p.
+34) speculates.
+\section{A Brief History of Artificial Intelligence}
+The preliminary work that makes AI possible dates back to the first attempts to create computers; however, these research studies were limited in theoretical knowledge until the more
+sophisticated hardware was developed.
+For instance, the invention of faster Central Processor Units ledresearchers to have more calculation power and create more detailed and elaborate algorithms (Bostrom, n.d.).
+Alan Turing, who is regarded the one who sets the basis for AI, created a test to question a machine's ability in its intelligence (Grebelsky, Lisin, \& Oks, n.d.).
+The second milestone of AI is invention of a programming language, Lisp (list processing), in the laboratories of Massachusetts Institute of Technology.
+Even though the concepts of AI existed before Lisp, it enabled researchers to use symbolic objects rather than numbers which was a major obstacle of AI creation.
+The other issue precluding the creation of AI is the challenges of information collection.
+As mentioned above, emulation of human cognitive and perceptual process have been a major method to implement AI.
+For that reason, natural language comprehension and visual information recognition have become two main focuses in AI research.
+Another example of the imitation of humanistic features is the structure of the human brain.
+The emergence of brand new sophisticated algorithms, namely, artificial neural networks and deep learning, also show significant resemblance to neural structure of the human brain which has
+enabled researchers to achieve more in the creation of AI. 
+\section{Advantages of Artificial Intelligence}
+Anthropomorphism is the basis of AI which is the imitation of the way that humans find solutions for problems.
+As a result of this imitation process, anticipated outcomes are not only solving the problem itself, but also finding the optimal solution for the problem in shortest time period possible.
+This speed and ability to solve problems will be advantageous for human kind.
+In this section, the advantages of AI are discussed.
+\subsection{Solutions for the Chronic Problems of Societies}
+Bryson (2015) claims that the common societal problems, such as the inequitable income distribution and poverty resulting from overpopulation, are impossible to cope with using regular tools and paradigms which governments now have.
+Having been scrutinizing social sciences, namely, developmental psychology and sociology, researchers might expand their interpretation of human behaviors which might enable them find new solutions for the given problems.
+Moreover, elimination of aging and eradication of diseases might be the possible consequence of the creation of AI (Bostrom, n.d.).
+Both authors discuss AI's advanced reasoning and interpretation underlining the new opportunities that AI might bring to societies in order to solve chronic societal problems.
+\subsection{The Last Invention of Human Kind That Researchers Forsee}
+By its definition, AI appears to provide the fastest and the optimal solutions for the problems that is given which depends on supreme decision-making and cognitive processes that of humans.
+Consequently, this advanced techniques will likely to provide a privilege to have our problems solved with the help of AI.
+In other words, thanks to outstripping abilities of AI, humans might not need to invent any other tool to solve problems (Bostrom, n.d.).
+\subsection{Singularity}
+Bostrom (n.d.) also discusses that AI might deliberately elaborate its structure and source code to enhance its abilities resulting in more advanced superintelligence, which will result in more complex structure of AI and calculation power.
+\subsection{Availability of Cloning}
+Since AI will notably rely on software implementations, it might be convenient to download its source code and promptly mount it on new hardware.
+That simplicity will likely to create more calculation power for the society and enable individuals to have personal robots.
+This possibility to create personal superintelligent agents with a cost of fractions of seconds and hardware.
+\section{Challenges Raised by AI}
+From the very beginning of the conceptual designs of AI, it has been the most debated issue in the engineering and scientific societies due to its ethical problems.
+Near future is fecund to a dilemma which human kind will face in AI's moral integrity and its position in society (Duffy, 2006).
+This section synthesizes the ethical issues and counterarguments coping with them.
+\subsection{Security Issues}
+Since robots can be regarded self-conscience agents, thanks to advanced reasoning, cognitive and perceptual abilities provided by AI, a major issue having been discussed is whether or not military, one of the biggest supporter of AI, is being sincere with its funding (Grebelsky et al., n.d.).
+Of the many supporters of AI, military appears to be the most questionable one due to plausible intentions of creation of humanoid army.
+The ultimate reason of AI which is elevation of life conditions and inquiry for the chronic problems of our societies notwithstanding, utilization of weaponized robotic army would increment the vast possession of ammunition and weaponization problem rather than solving our problems.\par
+Although being able to elaborate its source code by itself and being easily cloned are the factors considered advantage for the society, Grebelsky et al.
+(n.d.) claims that combination of these factors would make AI able to easily reproduce itself, which means robots may own robots that they create in the long term.
+Consequently, second generations robots created by the first generations would be utterly
+dependent on the first generation robots which means the first generation robots might command their offspring how ever they want.
+This unpredictable action-decision chain raises a major security problems including human annihilation for the society.
+\subsection{Socio-economic Issues}
+The rise of computers which has led the employment of robots in industry lessen the human employment starting from late 70's.
+Because of the downsizing tendency of corporation which resulted from this replacement, millions of low-skilled workers lost their jobs.
+Given that fact, Grebelsky et al.
+(n.d.) predicts the aftermath of the creation of AI.
+This vast computation power might replace most of the low-skilled laborers with the more powerful robots.
+In the light of that prediction, highly developed economies may show an extensive recession.\par
+Along with the economical effects of workplace computerization, eradication of low-skilled jobs may lead the expansion of the gap among the social groups.
+For instance, those who can use computers or know develop software have reached to higher classes in the societies.
+This expansion of gap among the social groups contradicts the societal goals of the creation of AI.\par
+In addition to former arguments, Rosas (2012) proposes yet another. Even though researchers, for instance, want to create a narrow-domain savvy robot, the robot may want to change its profession
+from the one that it had been taught or coded to a brand new one.
+This probable change of profession contradicts with the reason its creation purpose which may be interpreted as a act of disobey to its master.
+\subsection{Legal Issues}
+Since self-awareness of AI, it can be regarded as an independent agent.
+This conceptual independency, however, raises a ethical dilemma.
+Many researchers has been questioning whether or not superintelligent agents have duties to the society and to what extent governments give social rights Roberts (2004).
+Given that approach, Krebs (2006) mentions early speculations of social equality
+regarding civil and political rights among robots and humans in Japanese anime and mangas which artworks are consisted of futuristic plots including robots cohabitating and interacting with humans.
+These questions caused by the legal ramification of AI.
+Grebelsky (n.d.) discusses that it is not obvious that who will be responsible for results of AI's actions.
+Not only does AI's position in the society matter, but it is also equally important for governments to decide the AI's responsibility for the society, vice versa.
+\par
+The counterargument was proposed by Rosas (2012) by underlining the evolutionary approach on human morality.
+As Rosas (2012) cited, probability of error in evolution of human morality and nature displays a significant resemblance to the errors that might AI commit.
+For that reason, it is more logical to create a ground that can tolerate the probable AI's errors.
+\subsection{Religious Issues}
+One issue that discussed among scholars is whether or not creating a self-aware machine which is able to reason in the same level with human intelligence would be stealing the role of God.
+In addition to that issue, almost all of the monotheistic religions put significant emphasis on the features of God concept.
+According to these religions, God himself is unique and incomparably exceptional than the ones what he created.
+Of the many major sins, imitating God, or in other words one's God-like manifestation, is the unforgivable one.
+Grebelsky et al.
+(n.d.) discusses this issue by showing the similarities of creation of a self-aware agent and creation concept of God.
+Moreover, Duffy (2006) mentions human-like form that researchers tend to build social robots, an example of embodiment of AI.
+In the light of these facts, the concept of God and the creation of AI seems to intersect to some extent.\par
+The counterarguments put significance on more God and abilities that humans given by him rather than the limitations provided by the rules of religions.
+This approach to research and development of AI considers human and nature the masterpiece of God.
+For instance, brain is one the biggest resource that provided by God in order to make humans able to create tools and techniques to solve their problems, namely, taming the nature, building societies and elevating one's position in these societies.
+From this perspective, AI would be the best use of brain to commit what God orders (Grebelsky et al., n.d.).
+\section{Conclusion}
+As the research studies toward the creation of AI deepens, this technological advancements will raise more ethical problems.
+Regardless of the sources of issues, these problems relate to AI's definition and its responsibilities.
+It is crucially important to decide whether or not robots are simply functional machine that is utilitarian in its responsibilities and nothing more.
+If so, it is irrelevant to discuss the ethical problems arisen by its creation because the problems will become a question of accuracy of the source code.
+However, the results of recent studies indicate that in near future individuals may possess personal robots interacting closely with their master.
+In that case, the matter should be discussed would be how to prepare individuals, societies and governments its coming.
+As for the ethical problems, they will highly likely to be no more prone to erroneousness than any other human invention.
+If evolutionary and development psychology is taken into account, the first members of fully autonomous social robots, which are closely related to the terms of AI, will also evolve rapidly to its excellence.
+The only limitation in its experimental progress should be the initial motivations which must permanently coded to create anti-behaviors constraining its action-decision chain.
+\bibliographystyle{apacite}
+\bibliography{file.bib}
 \end{document}

### 2015-06-08 draft1.tex
Start Re-formating and Citing

@@
 \documentclass[man]{apa6}
-\title{Sample Title} %Change Title
+\title{Robots, Are They Overlords or Serf-Laborers?}
 \author{Murat Ambarkutuk}
@@
 \usepackage{apacite}
-\abstract{Of all the tools and methods invented by human kind to tame nature and make use of its challenges, the computer has had the greatest impact on society.
+% modify it!
+\abstract{Of all the tools and methods invented by humankind to tame nature and make use of its challenges, the computer has had the greatest impact on society.
 Coupled with the Internet, computers have changed the way billions of humans work, entertain themselves, and think.
@@
 Research toward the creation of AI includes creation of self-aware machines that have superior intellectual abilities to that of human abilities.
-However, many researchers argue that the creation of AI will deeply change the society and will help human kind to solve major societal problems, while others refute the arguments for the conceptual invention because of ethical problems that AI will bring such as an anticipated human annihilation by these agents.
+However, many researchers argue that the creation of AI will deeply change the society and it will help humankind to solve major societal problems, while others refute the arguments for the conceptual invention because of ethical problems that AI will bring such as an anticipated human annihilation by these agents.
 This paper focuses on the the ethical problems that the creation of AI will raise.}
 \keywords{artificial intelligence, robotics, ethics, society} 
-\shorttitle{Short Title as per APA manual} %Change it
+\shorttitle{Overlords vs. Serf-Laborers}
 \leftheader{Even-Numbered Page Header} %Change it
@@
 \maketitle
+\section{New Synthesis}
+Even though the term robot was coined two centuries ago and the idea of Artificial Intelligence (AI) emerged decades ago, some of the problems that have been raised by these two terms are yet to solved.
+Sometimes, solutions for any arbitrary problem can be solved by seeing the bigger picture rather than scrutinizing tiny details.
+Thus, this paper focuses on numerous definitions for these terms and various applications of AI.\par
+By literary definition the term robot is derived from the Czech word "roboti" meaning serf-labor.
+However, this slave-like definition has altered to something brand new as technology advances.
+In this article entitled "The Sheer Difficulty of Defining What a Robot Is", \citeA{pear} discusses two distinctive definitions of Robotics that are posed by the prominent experts in the field of Robotics.
+These two definitions emphasize different aspect of Robotics creating important distinctions among them.
+The first definition puts emphasis on the successful combination of a rigid body responsible from interacting with its environment and a central reasoning unit responsible from reasoning tasks based perception and cognition.
+Without software and hardware collaboration, as \citeA{pear} cited in his article, accomplishing such tasks for a robot cannot be possible.
+The second definition, however, takes autonomy into account.
+A robot, \citeA{pear} quoted in his article, must have an detailed idea of any action formed by a tedious plan, accurate reasoning and precise action to interact with its physical environment.
+In light of these definitions, robots have to interact with its environment, which exclude any means of social interactions.
+However, \citeA{lan} asserts that socially interaction robots are significantly popular among society.
+Albeit popular, social robots, for instance a teacher robot or a guidance robot employed in an art gallery, seem to be decontextualized.
+This discrepancy brings about a major problem in individual and societal level.
+For instance, individuals have started to get strong advices from AI applications rather than a close friend who know better about the individual seeking advices, the taste of of music or book for instance, than a software crunching numbers faster than a man.
+Even though this issue seems to have a minor flipside, once it is aggregated, it will create true alienation from society and confussion regarding personhood, \citeA{lan} claims.\par
 \section{Introduction}
@@
 As a result of this imitation process, anticipated outcomes are not only solving the problem itself, but also finding the optimal solution for the problem in shortest time period possible.
-This speed and ability to solve problems will be advantageous for human kind.
+This speed and ability to solve problems will be advantageous for humankind.
 In this section, the advantages of AI are discussed.
@@
 Both authors discuss AI's advanced reasoning and interpretation underlining the new opportunities that AI might bring to societies in order to solve chronic societal problems.
-\subsection{The Last Invention of Human Kind That Researchers Forsee}
+\subsection{The Last Invention of humankind That Researchers Forsee}
 By its definition, AI appears to provide the fastest and the optimal solutions for the problems that is given which depends on supreme decision-making and cognitive processes that of humans.
@@
 From the very beginning of the conceptual designs of AI, it has been the most debated issue in the engineering and scientific societies due to its ethical problems.
-Near future is fecund to a dilemma which human kind will face in AI's moral integrity and its position in society (Duffy, 2006).
+Near future is fecund to a dilemma which humankind will face in AI's moral integrity and its position in society (Duffy, 2006).
 This section synthesizes the ethical issues and counterarguments coping with them.
@@
 \bibliographystyle{apacite}
-\bibliography{file.bib}
+\bibliography{bibliography}
 \end{document}

### 2015-06-08 draft1.tex
Type in-class synthesis paper

@@
 Even though this issue seems to have a minor flipside, once it is aggregated, it will create true alienation from society and confussion regarding personhood, \citeA{lan} claims.\par
+Along with the definitions of Robotics, the applications of it extensively vary which makes it hard to define or understand the task and the responsibilities of robots.
+\citeA{lan} gives different examples from a software tailored for "Jeopardy" to a teacher robot.
+Although \citeA{pear} excludes any means of social interaction in the definitions of Robotics proposed in this article, \citeA(rod) exemplifies an emerging application of robotics, a molecular level robot which identifies cancerous cells and attach them by releasing antibodies, thereby eliminating cancerous cells.
+Even though, experts have not been able to solve dilemma within the field of robotics, this case of sophistication within Robotics exemplifies another complex issue.
+The reason why these social interaction dilemma matter, whether in bodily level or molecular level, is that technology advances in faster pace that of the wisdom regarding robots and ourselves.\par
+The notion of increasingly accelerating technology with the precious help of scientific research studies thrills individuals, and gives hope to patients.
+However, these two prominent terms of technology closely resembles another, the Internet.
+As the expansion and the accessibility to AI and Robotics increase, the prediction of the aftermath has become decreipt due to the late response of individuals and their wisdom toward these technologies.
+Thus, robotics and AI should be scrutinized to understand and formulate its definitions and functions, otherwise yet another issue will jump into debate topics before formers could be solved.
+
 \section{Introduction}

### 2015-06-09 draft1.tex
Format all citation w/ bibtex

@@
 \section{New Synthesis}
-Even though the term robot was coined two centuries ago and the idea of Artificial Intelligence (AI) emerged decades ago, some of the problems that have been raised by these two terms are yet to solved.
+\citeA{bost} \citeA{bry} \citeA{bob} \citeA{gre} \citeA{rosa} \citeA{duff}
+Even though the term robot was coined two centuries ago and the idea of (AI) emerged decades ago, some of the problems that have been raised by these two terms are yet to solved.
 Sometimes, solutions for any arbitrary problem can be solved by seeing the bigger picture rather than scrutinizing tiny details.
@@
 \citeA{lan} gives different examples from a software tailored for "Jeopardy" to a teacher robot.
-Although \citeA{pear} excludes any means of social interaction in the definitions of Robotics proposed in this article, \citeA(rod) exemplifies an emerging application of robotics, a molecular level robot which identifies cancerous cells and attach them by releasing antibodies, thereby eliminating cancerous cells.
+Although \citeA{pear} excludes any means of social interaction in the definitions of Robotics proposed in this article, \citeA{rodhan} exemplifies an emerging application of robotics, a molecular level robot which identifies cancerous cells and attach them by releasing antibodies, thereby eliminating cancerous cells.
 Even though, experts have not been able to solve dilemma within the field of robotics, this case of sophistication within Robotics exemplifies another complex issue.
@@
 Consequently, cognitive and perceptual systems of the human body have been scrutinized by researchers in order to emulate these processes at the hardware and software level.\par
-One common definition of AI is cited by Bostrom (n.d.), “A super-intelligence is any intellect that is vastly outperforms the best human brains in practically every field, including scientific creativity, general wisdom and social skills.” This definition clearly distinguishes specific domain intelligent agents and AI.
-Based on this definition a computer system, Deep Blue, which is a well-known computer system for its success in chess can be considered smart within a narrow domain rather than a genuine AI supported by limitations that Duffy (2006, p.
-34) speculates.
+One common definition of AI is cited by \citeA{bost}, "A super-intelligence is any intellect that is vastly outperforms the best human brains in practically every field, including scientific creativity, general wisdom and social skills." This definition clearly distinguishes specific domain intelligent agents and AI.
+Based on this definition a computer system, Deep Blue, which is a well-known computer system for its success in chess can be considered smart within a narrow domain rather than a genuine AI supported by limitations that \citeauthor{duff} \citeyear[p.~34]{duff} speculates.
 \section{A Brief History of Artificial Intelligence}
@@
 sophisticated hardware was developed.
-For instance, the invention of faster Central Processor Units ledresearchers to have more calculation power and create more detailed and elaborate algorithms (Bostrom, n.d.).
-Alan Turing, who is regarded the one who sets the basis for AI, created a test to question a machine's ability in its intelligence (Grebelsky, Lisin, \& Oks, n.d.).
+For instance, the invention of faster Central Processor Units led researchers to have more calculation power and create more detailed and elaborate algorithms \cite{bost} Alan Turing, who is regarded the one who sets the basis for AI, created a test to question a machine's ability in its intelligence \cite{gre}.
 The second milestone of AI is invention of a programming language, Lisp (list processing), in the laboratories of Massachusetts Institute of Technology.
@@
 \subsection{Solutions for the Chronic Problems of Societies}
-Bryson (2015) claims that the common societal problems, such as the inequitable income distribution and poverty resulting from overpopulation, are impossible to cope with using regular tools and paradigms which governments now have.
+\citeA{bry} claims that the common societal problems, such as the inequitable income distribution and poverty resulting from overpopulation, are impossible to cope with using regular tools and paradigms which governments now have.
 Having been scrutinizing social sciences, namely, developmental psychology and sociology, researchers might expand their interpretation of human behaviors which might enable them find new solutions for the given problems.
-Moreover, elimination of aging and eradication of diseases might be the possible consequence of the creation of AI (Bostrom, n.d.).
+Moreover, elimination of aging and eradication of diseases might be the possible consequence of the creation of AI /citeA{bost}.
 Both authors discuss AI's advanced reasoning and interpretation underlining the new opportunities that AI might bring to societies in order to solve chronic societal problems.
@@
 Consequently, this advanced techniques will likely to provide a privilege to have our problems solved with the help of AI.
-In other words, thanks to outstripping abilities of AI, humans might not need to invent any other tool to solve problems (Bostrom, n.d.).
+In other words, thanks to outstripping abilities of AI, humans might not need to invent any other tool to solve problems \cite{bost}.
 \subsection{Singularity}
-Bostrom (n.d.) also discusses that AI might deliberately elaborate its structure and source code to enhance its abilities resulting in more advanced superintelligence, which will result in more complex structure of AI and calculation power.
+\citeA{bost} also discusses that AI might deliberately elaborate its structure and source code to enhance its abilities resulting in more advanced superintelligence, which will result in more complex structure of AI and calculation power.
 \subsection{Availability of Cloning}
@@
 From the very beginning of the conceptual designs of AI, it has been the most debated issue in the engineering and scientific societies due to its ethical problems.
-Near future is fecund to a dilemma which humankind will face in AI's moral integrity and its position in society (Duffy, 2006).
+Near future is fecund to a dilemma which humankind will face in AI's moral integrity and its position in society \cite{duff}.
 This section synthesizes the ethical issues and counterarguments coping with them.
 \subsection{Security Issues}
-Since robots can be regarded self-conscience agents, thanks to advanced reasoning, cognitive and perceptual abilities provided by AI, a major issue having been discussed is whether or not military, one of the biggest supporter of AI, is being sincere with its funding (Grebelsky et al., n.d.).
+Since robots can be regarded self-conscience agents, thanks to advanced reasoning, cognitive and perceptual abilities provided by AI, a major issue having been discussed is whether or not military, one of the biggest supporter of AI, is being sincere with its funding \cite{gre}.
 Of the many supporters of AI, military appears to be the most questionable one due to plausible intentions of creation of humanoid army.
 The ultimate reason of AI which is elevation of life conditions and inquiry for the chronic problems of our societies notwithstanding, utilization of weaponized robotic army would increment the vast possession of ammunition and weaponization problem rather than solving our problems.\par
-Although being able to elaborate its source code by itself and being easily cloned are the factors considered advantage for the society, Grebelsky et al.
-(n.d.) claims that combination of these factors would make AI able to easily reproduce itself, which means robots may own robots that they create in the long term.
+Although being able to elaborate its source code by itself and being easily cloned are the factors considered advantage for the society, \citeA{duff} claims that combination of these factors would make AI able to easily reproduce itself, which means robots may own robots that they create in the long term.
 Consequently, second generations robots created by the first generations would be utterly
@@
 Because of the downsizing tendency of corporation which resulted from this replacement, millions of low-skilled workers lost their jobs.
-Given that fact, Grebelsky et al.
-(n.d.) predicts the aftermath of the creation of AI.
+Given that fact, \citeA{gre} predicts the aftermath of the creation of AI.
 This vast computation power might replace most of the low-skilled laborers with the more powerful robots.
@@
 This expansion of gap among the social groups contradicts the societal goals of the creation of AI.\par
-In addition to former arguments, Rosas (2012) proposes yet another. Even though researchers, for instance, want to create a narrow-domain savvy robot, the robot may want to change its profession
+In addition to former arguments, \citeA{rosa} proposes yet another. Even though researchers, for instance, want to create a narrow-domain savvy robot, the robot may want to change its profession
 from the one that it had been taught or coded to a brand new one.
@@
 This conceptual independency, however, raises a ethical dilemma.
-Many researchers has been questioning whether or not superintelligent agents have duties to the society and to what extent governments give social rights Roberts (2004).
-Given that approach, Krebs (2006) mentions early speculations of social equality
-regarding civil and political rights among robots and humans in Japanese anime and mangas which artworks are consisted of futuristic plots including robots cohabitating and interacting with humans.
+Many researchers has been questioning whether or not superintelligent agents have duties to the society and to what extent governments give social rights \cite{bob}.
+Given that approach, \cite{kerb} mentions early speculations of social equality regarding civil and political rights among robots and humans in Japanese anime and mangas which artworks are consisted of futuristic plots including robots cohabitating and interacting with humans.
 These questions caused by the legal ramification of AI.
-Grebelsky (n.d.) discusses that it is not obvious that who will be responsible for results of AI's actions.
+\citeA{gre} discusses that it is not obvious that who will be responsible for results of AI's actions.
 Not only does AI's position in the society matter, but it is also equally important for governments to decide the AI's responsibility for the society, vice versa.
 \par
-The counterargument was proposed by Rosas (2012) by underlining the evolutionary approach on human morality.
-As Rosas (2012) cited, probability of error in evolution of human morality and nature displays a significant resemblance to the errors that might AI commit.
+The counterargument was proposed by \citeA{rosa} by underlining the evolutionary approach on human morality.
+As \citeA{rosa} cited, probability of error in evolution of human morality and nature displays a significant resemblance to the errors that might AI commit.
 For that reason, it is more logical to create a ground that can tolerate the probable AI's errors.
@@
 According to these religions, God himself is unique and incomparably exceptional than the ones what he created.
-Of the many major sins, imitating God, or in other words one's God-like manifestation, is the unforgivable one.
-Grebelsky et al.
-(n.d.) discusses this issue by showing the similarities of creation of a self-aware agent and creation concept of God.
-Moreover, Duffy (2006) mentions human-like form that researchers tend to build social robots, an example of embodiment of AI.
+Of the many major sins, imitating God, or in other words one's God-like manifestation, is the unforgivable one.\citeA{gre} discusses this issue by showing the similarities of creation of a self-aware agent and creation concept of God.
+Moreover, \citeA{duff} mentions human-like form that researchers tend to build social robots, an example of embodiment of AI.
 In the light of these facts, the concept of God and the creation of AI seems to intersect to some extent.\par
@@
 For instance, brain is one the biggest resource that provided by God in order to make humans able to create tools and techniques to solve their problems, namely, taming the nature, building societies and elevating one's position in these societies.
-From this perspective, AI would be the best use of brain to commit what God orders (Grebelsky et al., n.d.).
+From this perspective, AI would be the best use of brain to commit what God orders \cite{gre}.
 \section{Conclusion}

### 2015-06-09 draft1.tex
Add a page break between old and new paper
Start to merge two paper in a logical sequence

@@
 \maketitle
-\section{New Synthesis}
-\citeA{bost} \citeA{bry} \citeA{bob} \citeA{gre} \citeA{rosa} \citeA{duff}
-Even though the term robot was coined two centuries ago and the idea of (AI) emerged decades ago, some of the problems that have been raised by these two terms are yet to solved.
-Sometimes, solutions for any arbitrary problem can be solved by seeing the bigger picture rather than scrutinizing tiny details.
-Thus, this paper focuses on numerous definitions for these terms and various applications of AI.\par
-By literary definition the term robot is derived from the Czech word "roboti" meaning serf-labor.
-However, this slave-like definition has altered to something brand new as technology advances.
-In this article entitled "The Sheer Difficulty of Defining What a Robot Is", \citeA{pear} discusses two distinctive definitions of Robotics that are posed by the prominent experts in the field of Robotics.
-These two definitions emphasize different aspect of Robotics creating important distinctions among them.
-The first definition puts emphasis on the successful combination of a rigid body responsible from interacting with its environment and a central reasoning unit responsible from reasoning tasks based perception and cognition.
-Without software and hardware collaboration, as \citeA{pear} cited in his article, accomplishing such tasks for a robot cannot be possible.
-The second definition, however, takes autonomy into account.
-A robot, \citeA{pear} quoted in his article, must have an detailed idea of any action formed by a tedious plan, accurate reasoning and precise action to interact with its physical environment.
-In light of these definitions, robots have to interact with its environment, which exclude any means of social interactions.
-However, \citeA{lan} asserts that socially interaction robots are significantly popular among society.
-Albeit popular, social robots, for instance a teacher robot or a guidance robot employed in an art gallery, seem to be decontextualized.
-This discrepancy brings about a major problem in individual and societal level.
-For instance, individuals have started to get strong advices from AI applications rather than a close friend who know better about the individual seeking advices, the taste of of music or book for instance, than a software crunching numbers faster than a man.
-Even though this issue seems to have a minor flipside, once it is aggregated, it will create true alienation from society and confussion regarding personhood, \citeA{lan} claims.\par
-Along with the definitions of Robotics, the applications of it extensively vary which makes it hard to define or understand the task and the responsibilities of robots.
-\citeA{lan} gives different examples from a software tailored for "Jeopardy" to a teacher robot.
-Although \citeA{pear} excludes any means of social interaction in the definitions of Robotics proposed in this article, \citeA{rodhan} exemplifies an emerging application of robotics, a molecular level robot which identifies cancerous cells and attach them by releasing antibodies, thereby eliminating cancerous cells.
-Even though, experts have not been able to solve dilemma within the field of robotics, this case of sophistication within Robotics exemplifies another complex issue.
-The reason why these social interaction dilemma matter, whether in bodily level or molecular level, is that technology advances in faster pace that of the wisdom regarding robots and ourselves.\par
-The notion of increasingly accelerating technology with the precious help of scientific research studies thrills individuals, and gives hope to patients.
-However, these two prominent terms of technology closely resembles another, the Internet.
-As the expansion and the accessibility to AI and Robotics increase, the prediction of the aftermath has become decreipt due to the late response of individuals and their wisdom toward these technologies.
-Thus, robotics and AI should be scrutinized to understand and formulate its definitions and functions, otherwise yet another issue will jump into debate topics before formers could be solved.
-
+% Citing examples \citeA{bost} \citeA{bry} \citeA{bob} \citeA{gre} \citeA{rosa} \citeA{duff}
 \section{Introduction}
+\subsection{v1}
 Although AI is a research topic in the fields of engineering and science, the first introduction of it was fictional literary and futuristic artistic works.
-For that reason, its popularity significantly
-ascended which resulted in becoming perhaps the most debated technology related term in the last century.
+For that reason, its popularity significantly ascended which resulted in becoming perhaps the most debated technology related term in the last century.
 Despite AI's popularity, it may be the most misunderstood term that in the field of engineering.
@@
 Based on this definition a computer system, Deep Blue, which is a well-known computer system for its success in chess can be considered smart within a narrow domain rather than a genuine AI supported by limitations that \citeauthor{duff} \citeyear[p.~34]{duff} speculates.
+\subsection{v2}
+Even though the term robot was coined two centuries ago and the idea of AI emerged decades ago, some of the problems that have been raised by these two terms are yet to be solved.
+Sometimes, solutions for any arbitrary problem can be solved by seeing the bigger picture rather than scrutinizing tiny details.
+Thus, this paper focuses on numerous definitions for these terms and various applications of them which create intricacies and challenges in many level, varying from individual to societal level.\par
+Formation (As it follows: \#\#, \#\#, \#\#)
 \section{A Brief History of Artificial Intelligence}
-The preliminary work that makes AI possible dates back to the first attempts to create computers; however, these research studies were limited in theoretical knowledge until the more
-sophisticated hardware was developed.
+The preliminary work that makes AI possible dates back to the first attempts to create computers; however, these research studies were limited in theoretical knowledge until the more sophisticated hardware was developed.
 For instance, the invention of faster Central Processor Units led researchers to have more calculation power and create more detailed and elaborate algorithms \cite{bost} Alan Turing, who is regarded the one who sets the basis for AI, created a test to question a machine's ability in its intelligence \cite{gre}.
@@
 Another example of the imitation of humanistic features is the structure of the human brain.
-The emergence of brand new sophisticated algorithms, namely, artificial neural networks and deep learning, also show significant resemblance to neural structure of the human brain which has
-enabled researchers to achieve more in the creation of AI. 
+The emergence of brand new sophisticated algorithms, namely, artificial neural networks and deep learning, also show significant resemblance to neural structure of the human brain which has enabled researchers to achieve more in the creation of AI.
 \section{Advantages of Artificial Intelligence}
@@
 Although being able to elaborate its source code by itself and being easily cloned are the factors considered advantage for the society, \citeA{duff} claims that combination of these factors would make AI able to easily reproduce itself, which means robots may own robots that they create in the long term.
-Consequently, second generations robots created by the first generations would be utterly
-dependent on the first generation robots which means the first generation robots might command their offspring how ever they want.
+Consequently, second generations robots created by the first generations would be utterly dependent on the first generation robots which means the first generation robots might command their offspring how ever they want.
 This unpredictable action-decision chain raises a major security problems including human annihilation for the society.
@@
 This expansion of gap among the social groups contradicts the societal goals of the creation of AI.\par
-In addition to former arguments, \citeA{rosa} proposes yet another. Even though researchers, for instance, want to create a narrow-domain savvy robot, the robot may want to change its profession
-from the one that it had been taught or coded to a brand new one.
+In addition to former arguments, \citeA{rosa} proposes yet another.
+Even though researchers, for instance, want to create a narrow-domain savvy robot, the robot may want to change its profession from the one that it had been taught or coded to a brand new one.
 This probable change of profession contradicts with the reason its creation purpose which may be interpreted as a act of disobey to its master.
@@
 From this perspective, AI would be the best use of brain to commit what God orders \cite{gre}.
+\section{The Bigger Picture}
+\subsection{What is a Robot?}
+By literary definition the term robot is derived from the Czech word "roboti" meaning serf-labor.
+However, this slave-like definition has altered to something brand new as technology advances.
+In this article entitled "The Sheer Difficulty of Defining What a Robot Is", \citeA{pear} discusses two distinctive definitions of Robotics that are posed by the prominent experts in the field of Robotics.
+These two definitions emphasize different aspect of Robotics creating important distinctions among them.
+The first definition puts emphasis on the successful combination of a rigid body responsible from interacting with its environment and a central reasoning unit responsible from reasoning tasks based perception and cognition.
+Without software and hardware collaboration, as \citeA{pear} cited in his article, accomplishing such tasks for a robot cannot be possible.
+The second definition, however, takes autonomy into account.
+A robot, \citeA{pear} quoted in his article, must have an detailed idea of any action formed by a tedious plan, accurate reasoning and precise action to interact with its physical environment.
+In light of these definitions, robots have to interact with its environment, which exclude any means of social interactions.
+However, \citeA{lan} asserts that socially interaction robots are significantly popular among society.
+Albeit popular, social robots, for instance a teacher robot or a guidance robot employed in an art gallery, seem to be decontextualized.
+This discrepancy brings about a major problem in individual and societal level.
+For instance, individuals have started to get strong advices from AI applications rather than a close friend who know better about the individual seeking advices, the taste of of music or book for instance, than a software crunching numbers faster than a man.
+Even though this issue seems to have a minor flipside, once it is aggregated, it will create true alienation from society and confussion regarding personhood, \citeA{lan} claims.\par
+\subsection{What (should) does a Robot do?}
+Along with the definitions of Robotics, the applications of it extensively vary which makes it hard to define or understand the task and the responsibilities of robots.
+\citeA{lan} gives different examples from a software tailored for "Jeopardy" to a teacher robot.
+Although \citeA{pear} excludes any means of social interaction in the definitions of Robotics proposed in this article, \citeA{rodhan} exemplifies an emerging application of robotics, a molecular level robot which identifies cancerous cells and attach them by releasing antibodies, thereby eliminating cancerous cells.
+Even though, experts have not been able to solve dilemma within the field of robotics, this case of sophistication within Robotics exemplifies another complex issue.
+The reason why these social interaction dilemma matter, whether in bodily level or molecular level, is that technology advances in faster pace that of the wisdom regarding robots and ourselves.\par
+
 \section{Conclusion}
+\subsection{v1}
 As the research studies toward the creation of AI deepens, this technological advancements will raise more ethical problems.
@@
 The only limitation in its experimental progress should be the initial motivations which must permanently coded to create anti-behaviors constraining its action-decision chain.
+\subsection{v2}
+The notion of increasingly accelerating technology with the precious help of scientific research studies thrills individuals, and gives hope to patients.
+However, these two prominent terms of technology closely resembles another, the Internet.
+As the expansion and the accessibility to AI and Robotics increase, the prediction of the aftermath has become decreipt due to the late response of individuals and their wisdom toward these technologies.
+Thus, robotics and AI should be scrutinized to understand and formulate its definitions and functions, otherwise yet another issue will jump into debate topics before formers could be solved.
 \bibliographystyle{apacite}

### 2015-06-10 draft1.tex
Merge two papers cohessively

@@
 \affiliation{English Language Institute, University of Delaware \\ murata@udel.edu}
-\note{First Draft; 6/8/2015}
+\note{First Draft; 6/8/2015; \LaTeX}
 \usepackage{apacite}
@@
 \section{Introduction}
-\subsection{v1}
-Although AI is a research topic in the fields of engineering and science, the first introduction of it was fictional literary and futuristic artistic works.
-For that reason, its popularity significantly ascended which resulted in becoming perhaps the most debated technology related term in the last century.
-Despite AI's popularity, it may be the most misunderstood term that in the field of engineering.
-In order to make clear its obfuscated definition, the tasks of AI should be mentioned.
-The task of AI is to create methods to enable machines to obtain symbolic data sets and manipulate them in order to solve generic problems in the most energy efficient and fastest fashion.
-The theory suggests that it is possible to achieve by imitating the processes of logical reasoning and decision making.
-Consequently, cognitive and perceptual systems of the human body have been scrutinized by researchers in order to emulate these processes at the hardware and software level.\par
-One common definition of AI is cited by \citeA{bost}, "A super-intelligence is any intellect that is vastly outperforms the best human brains in practically every field, including scientific creativity, general wisdom and social skills." This definition clearly distinguishes specific domain intelligent agents and AI.
-Based on this definition a computer system, Deep Blue, which is a well-known computer system for its success in chess can be considered smart within a narrow domain rather than a genuine AI supported by limitations that \citeauthor{duff} \citeyear[p.~34]{duff} speculates.
-\subsection{v2}
 Even though the term robot was coined two centuries ago and the idea of AI emerged decades ago, some of the problems that have been raised by these two terms are yet to be solved.
@@
 \subsection{What is a Robot?}
+One common definition of AI is cited by \citeA{bost}, "A super-intelligence is any intellect that is vastly outperforms the best human brains in practically every field, including scientific creativity, general wisdom and social skills." This definition clearly distinguishes specific domain intelligent agents and AI.
+Based on this definition a computer system, Deep Blue, which is a well-known computer system for its success in chess can be considered smart within a narrow domain rather than a genuine AI supported by limitations that \citeauthor{duff} \citeyear[p.~34]{duff} speculates.\par
 By literary definition the term robot is derived from the Czech word "roboti" meaning serf-labor.
@@
 \subsection{What (should) does a Robot do?}
+% A strip from the old paper
+In order to make clear its obfuscated definition, the tasks of AI should be addressed.
+The task of AI is to create methods to enable machines to obtain symbolic data sets and manipulate them in order to solve generic problems in the most energy efficient and fastest fashion.
+The theory suggests that it is possible to achieve by imitating the processes of logical reasoning and decision making.
+Consequently, cognitive and perceptual systems of the human body have been scrutinized by researchers in order to emulate these processes at the hardware and software level.\par
 Along with the definitions of Robotics, the applications of it extensively vary which makes it hard to define or understand the task and the responsibilities of robots.

### 2015-06-10 draft1.tex
Final Commit for 6/9/15

@@
+% plagiarism check
+% cohesion check
+% grammar check (firt two page of new paper)
 \documentclass[man]{apa6}
@@
 By literary definition the term robot is derived from the Czech word "roboti" meaning serf-labor.
-However, this slave-like definition has altered to something brand new as technology advances.
-In this article entitled "The Sheer Difficulty of Defining What a Robot Is", \citeA{pear} discusses two distinctive definitions of Robotics that are posed by the prominent experts in the field of Robotics.
-These two definitions emphasize different aspect of Robotics creating important distinctions among them.
+However, this definition closely refering to slave-like labourer has altered to something brand new as technology advances.
+In this article entitled "The Sheer Difficulty of Defining What a Robot Is", \citeA{pear} discusses two distinctive definitions of robotics that are posed by the prominent experts in the field of robotics.
+These two definitions emphasize different aspect of robotics creating important distinctions among them.
 The first definition puts emphasis on the successful combination of a rigid body responsible from interacting with its environment and a central reasoning unit responsible from reasoning tasks based perception and cognition.
@@
 Consequently, cognitive and perceptual systems of the human body have been scrutinized by researchers in order to emulate these processes at the hardware and software level.\par
-Along with the definitions of Robotics, the applications of it extensively vary which makes it hard to define or understand the task and the responsibilities of robots.
+Along with the definitions of robotics, the applications of it extensively vary which makes it hard to define or understand the task and the responsibilities of robots.
 \citeA{lan} gives different examples from a software tailored for "Jeopardy" to a teacher robot.
-Although \citeA{pear} excludes any means of social interaction in the definitions of Robotics proposed in this article, \citeA{rodhan} exemplifies an emerging application of robotics, a molecular level robot which identifies cancerous cells and attach them by releasing antibodies, thereby eliminating cancerous cells.
-Even though, experts have not been able to solve dilemma within the field of robotics, this case of sophistication within Robotics exemplifies another complex issue.
+Although \citeA{pear} excludes any means of social interaction in the definitions of robotics proposed in this article, \citeA{rodhan} exemplifies an emerging application of robotics, a molecular level robot which identifies cancerous cells and attach them by releasing antibodies, thereby eliminating cancerous cells.
+Even though, experts have not been able to solve dilemma within the field of robotics, this case of sophistication within robotics exemplifies another complex issue.
 The reason why these social interaction dilemma matter, whether in bodily level or molecular level, is that technology advances in faster pace that of the wisdom regarding robots and ourselves.\par
@@
 \section{Conclusion}
-\subsection{v1}
-As the research studies toward the creation of AI deepens, this technological advancements will raise more ethical problems.
-Regardless of the sources of issues, these problems relate to AI's definition and its responsibilities.
-It is crucially important to decide whether or not robots are simply functional machine that is utilitarian in its responsibilities and nothing more.
-If so, it is irrelevant to discuss the ethical problems arisen by its creation because the problems will become a question of accuracy of the source code.
-However, the results of recent studies indicate that in near future individuals may possess personal robots interacting closely with their master.
+The notion of increasingly accelerating technology with the precious help of scientific research studies thrills individuals, and gives hope to patients.
+%However, these two prominent terms of technology closely resembles another, the Internet.
+%, otherwise yet another issue will jump into debate topics before formers could be solved. 
+Yet, it is crucially important to decide whether or not robots are simply functional machines that are utilitarian in their responsibilities and nothing more.
+If so, it is irrelevant to discuss the ethical problems arisen by its creation because the problems will become a question of accuracy of the source code that runs robots and forms AI.
 In that case, the matter should be discussed would be how to prepare individuals, societies and governments its coming.
 As for the ethical problems, they will highly likely to be no more prone to erroneousness than any other human invention.
-If evolutionary and development psychology is taken into account, the first members of fully autonomous social robots, which are closely related to the terms of AI, will also evolve rapidly to its excellence.
-The only limitation in its experimental progress should be the initial motivations which must permanently coded to create anti-behaviors constraining its action-decision chain.
-\subsection{v2}
-The notion of increasingly accelerating technology with the precious help of scientific research studies thrills individuals, and gives hope to patients.
-However, these two prominent terms of technology closely resembles another, the Internet.
-As the expansion and the accessibility to AI and Robotics increase, the prediction of the aftermath has become decreipt due to the late response of individuals and their wisdom toward these technologies.
+If evolutionary and development psychology is taken into account, the first members of fully autonomous social robots will also evolve rapidly to their excellence.
+As the expansion and the accessibility to AI and robotics increase, the prediction of the aftermath has become decrepit due to the late response of individuals and their wisdom toward these technologies.
 Thus, robotics and AI should be scrutinized to understand and formulate its definitions and functions, otherwise yet another issue will jump into debate topics before formers could be solved.

### 2015-06-10 draft1.tex
Delete most of the parts coming from 1st paper

@@
 % modify it!
-\abstract{Of all the tools and methods invented by humankind to tame nature and make use of its challenges, the computer has had the greatest impact on society.
+\abstract{Of all the tools and methods invented by humankind to tame nature and make use of its challenges, the invention of computer has had the greatest impact on society.
 Coupled with the Internet, computers have changed the way billions of humans work, entertain themselves, and think.
 Since the rise of the computers, Artificial Intelligence (AI) has been one of the most debated issues in the field of engineering.
-Research toward the creation of AI includes creation of self-aware machines that have superior intellectual abilities to that of human abilities.
+Research toward the creation of AI includes a creation of self-aware machines that have superior intellectual abilities to that of human abilities.
 However, many researchers argue that the creation of AI will deeply change the society and it will help humankind to solve major societal problems, while others refute the arguments for the conceptual invention because of ethical problems that AI will bring such as an anticipated human annihilation by these agents.
@@
 Sometimes, solutions for any arbitrary problem can be solved by seeing the bigger picture rather than scrutinizing tiny details.
-Thus, this paper focuses on numerous definitions for these terms and various applications of them which create intricacies and challenges in many level, varying from individual to societal level.\par
-Formation (As it follows: \#\#, \#\#, \#\#)
-\section{A Brief History of Artificial Intelligence}
-The preliminary work that makes AI possible dates back to the first attempts to create computers; however, these research studies were limited in theoretical knowledge until the more sophisticated hardware was developed.
+Thus, this paper focuses on numerous definitions for these terms and various applications of them which create intricacies and challenges in many level, varying from individual to societal level.
+Formation of this paper is as it follows: \#\#, \#\#, \#\#
+%\section{A Brief History of Artificial Intelligence}
+%The preliminary work that makes AI possible dates back to the first attempts to create computers; however, these research studies were limited in theoretical knowledge until the more sophisticated hardware was developed.
 For instance, the invention of faster Central Processor Units led researchers to have more calculation power and create more detailed and elaborate algorithms \cite{bost} Alan Turing, who is regarded the one who sets the basis for AI, created a test to question a machine's ability in its intelligence \cite{gre}.
@@
 The emergence of brand new sophisticated algorithms, namely, artificial neural networks and deep learning, also show significant resemblance to neural structure of the human brain which has enabled researchers to achieve more in the creation of AI.
-\section{Advantages of Artificial Intelligence}
-Anthropomorphism is the basis of AI which is the imitation of the way that humans find solutions for problems.
+%\section{Advantages of Artificial Intelligence}
+%Anthropomorphism is the basis of AI which is the imitation of the way that humans find solutions for problems.
 As a result of this imitation process, anticipated outcomes are not only solving the problem itself, but also finding the optimal solution for the problem in shortest time period possible.
@@
 In this section, the advantages of AI are discussed.
-\subsection{Solutions for the Chronic Problems of Societies}
-\citeA{bry} claims that the common societal problems, such as the inequitable income distribution and poverty resulting from overpopulation, are impossible to cope with using regular tools and paradigms which governments now have.
+%\subsection{Solutions for the Chronic Problems of Societies}
+%\citeA{bry} claims that the common societal problems, such as the inequitable income distribution and poverty resulting from overpopulation, are impossible to cope with using regular tools and paradigms which governments now have.
 Having been scrutinizing social sciences, namely, developmental psychology and sociology, researchers might expand their interpretation of human behaviors which might enable them find new solutions for the given problems.
-Moreover, elimination of aging and eradication of diseases might be the possible consequence of the creation of AI /citeA{bost}.
+Moreover, elimination of aging and eradication of diseases might be the possible consequence of the creation of AI \citeA{bost}.
 Both authors discuss AI's advanced reasoning and interpretation underlining the new opportunities that AI might bring to societies in order to solve chronic societal problems.
-\subsection{The Last Invention of humankind That Researchers Forsee}
-By its definition, AI appears to provide the fastest and the optimal solutions for the problems that is given which depends on supreme decision-making and cognitive processes that of humans.
+%\subsection{The Last Invention of Humankind That Researchers Forsee}
+%By its definition, AI appears to provide the fastest and the optimal solutions for the problems that is given which depends on supreme decision-making and cognitive processes that of humans.
 Consequently, this advanced techniques will likely to provide a privilege to have our problems solved with the help of AI.
 In other words, thanks to outstripping abilities of AI, humans might not need to invent any other tool to solve problems \cite{bost}.
-\subsection{Singularity}
-\citeA{bost} also discusses that AI might deliberately elaborate its structure and source code to enhance its abilities resulting in more advanced superintelligence, which will result in more complex structure of AI and calculation power.
-\subsection{Availability of Cloning}
-Since AI will notably rely on software implementations, it might be convenient to download its source code and promptly mount it on new hardware.
+%\subsection{Singularity}
+%\citeA{bost} also discusses that AI might deliberately elaborate its structure and source code to enhance its abilities resulting in more advanced superintelligence, which will result in more complex structure of AI and calculation power.
+%\subsection{Availability of Cloning}
+%Since AI will notably rely on software implementations, it might be convenient to download its source code and promptly mount it on new hardware.
 That simplicity will likely to create more calculation power for the society and enable individuals to have personal robots.
 This possibility to create personal superintelligent agents with a cost of fractions of seconds and hardware.
-\section{Challenges Raised by AI}
-From the very beginning of the conceptual designs of AI, it has been the most debated issue in the engineering and scientific societies due to its ethical problems.
+%\section{Challenges Raised by AI}
+%From the very beginning of the conceptual designs of AI, it has been the most debated issue in the engineering and scientific societies due to its ethical problems.
 Near future is fecund to a dilemma which humankind will face in AI's moral integrity and its position in society \cite{duff}.
 This section synthesizes the ethical issues and counterarguments coping with them.
-\subsection{Security Issues}
-Since robots can be regarded self-conscience agents, thanks to advanced reasoning, cognitive and perceptual abilities provided by AI, a major issue having been discussed is whether or not military, one of the biggest supporter of AI, is being sincere with its funding \cite{gre}.
+%\subsection{Security Issues}
+%Since robots can be regarded self-conscience agents, thanks to advanced reasoning, cognitive and perceptual abilities provided by AI, a major issue having been discussed is whether or not military, one of the biggest supporter of AI, is being sincere with its funding \cite{gre}.
 Of the many supporters of AI, military appears to be the most questionable one due to plausible intentions of creation of humanoid army.
 The ultimate reason of AI which is elevation of life conditions and inquiry for the chronic problems of our societies notwithstanding, utilization of weaponized robotic army would increment the vast possession of ammunition and weaponization problem rather than solving our problems.\par
-Although being able to elaborate its source code by itself and being easily cloned are the factors considered advantage for the society, \citeA{duff} claims that combination of these factors would make AI able to easily reproduce itself, which means robots may own robots that they create in the long term.
+%Although being able to elaborate its source code by itself and being easily cloned are the factors considered advantage for the society, \citeA{duff} claims that combination of these factors would make AI able to easily reproduce itself, which means robots may own robots that they create in the long term.
 Consequently, second generations robots created by the first generations would be utterly dependent on the first generation robots which means the first generation robots might command their offspring how ever they want.
 This unpredictable action-decision chain raises a major security problems including human annihilation for the society.
-\subsection{Socio-economic Issues}
-The rise of computers which has led the employment of robots in industry lessen the human employment starting from late 70's.
+%\subsection{Socio-economic Issues}
+%The rise of computers which has led the employment of robots in industry lessen the human employment starting from late 70's.
 Because of the downsizing tendency of corporation which resulted from this replacement, millions of low-skilled workers lost their jobs.
@@
 In the light of that prediction, highly developed economies may show an extensive recession.\par
-Along with the economical effects of workplace computerization, eradication of low-skilled jobs may lead the expansion of the gap among the social groups.
+%Along with the economical effects of workplace computerization, eradication of low-skilled jobs may lead the expansion of the gap among the social groups.
 For instance, those who can use computers or know develop software have reached to higher classes in the societies.
 This expansion of gap among the social groups contradicts the societal goals of the creation of AI.\par
-In addition to former arguments, \citeA{rosa} proposes yet another.
+%In addition to former arguments, \citeA{rosa} proposes yet another.
 Even though researchers, for instance, want to create a narrow-domain savvy robot, the robot may want to change its profession from the one that it had been taught or coded to a brand new one.
 This probable change of profession contradicts with the reason its creation purpose which may be interpreted as a act of disobey to its master.
-\subsection{Legal Issues}
-Since self-awareness of AI, it can be regarded as an independent agent.
+%\subsection{Legal Issues}
+%Since self-awareness of AI, it can be regarded as an independent agent.
 This conceptual independency, however, raises a ethical dilemma.
@@
 \par
-The counterargument was proposed by \citeA{rosa} by underlining the evolutionary approach on human morality.
+%The counterargument was proposed by \citeA{rosa} by underlining the evolutionary approach on human morality.
 As \citeA{rosa} cited, probability of error in evolution of human morality and nature displays a significant resemblance to the errors that might AI commit.
 For that reason, it is more logical to create a ground that can tolerate the probable AI's errors.
-\subsection{Religious Issues}
-One issue that discussed among scholars is whether or not creating a self-aware machine which is able to reason in the same level with human intelligence would be stealing the role of God.
+%\subsection{Religious Issues}
+%One issue that discussed among scholars is whether or not creating a self-aware machine which is able to reason in the same level with human intelligence would be stealing the role of God.
 In addition to that issue, almost all of the monotheistic religions put significant emphasis on the features of God concept.
@@
 In the light of these facts, the concept of God and the creation of AI seems to intersect to some extent.\par
-The counterarguments put significance on more God and abilities that humans given by him rather than the limitations provided by the rules of religions.
+%The counterarguments put significance on more God and abilities that humans given by him rather than the limitations provided by the rules of religions.
 This approach to research and development of AI considers human and nature the masterpiece of God.
@@
 Based on this definition a computer system, Deep Blue, which is a well-known computer system for its success in chess can be considered smart within a narrow domain rather than a genuine AI supported by limitations that \citeauthor{duff} \citeyear[p.~34]{duff} speculates.\par
+
 By literary definition the term robot is derived from the Czech word "roboti" meaning serf-labor.
 However, this definition closely refering to slave-like labourer has altered to something brand new as technology advances.
-In this article entitled "The Sheer Difficulty of Defining What a Robot Is", \citeA{pear} discusses two distinctive definitions of robotics that are posed by the prominent experts in the field of robotics.
+In his article entitled "The Sheer Difficulty of Defining What a Robot Is", \citeA{pear} discusses two distinctive definitions of robotics that are posed by the prominent experts in the field of robotics.
 These two definitions emphasize different aspect of robotics creating important distinctions among them.
-The first definition puts emphasis on the successful combination of a rigid body responsible from interacting with its environment and a central reasoning unit responsible from reasoning tasks based perception and cognition.
-Without software and hardware collaboration, as \citeA{pear} cited in his article, accomplishing such tasks for a robot cannot be possible.
+The first definition puts emphasis on the successful combination of a rigid body responsible for interacting with its environment and a central reasoning unit responsible for reasoning tasks based perception and cognition.
+Without s software and hardware collaboration, as \citeA{pear} cited in his article, accomplishing its tasks for a robot cannot be possible.
 The second definition, however, takes autonomy into account.

### 2015-06-11 draft1.tex
Add Lin et al to bibliography.
Replace hidden parts to the end to have a better overall look

@@
 \maketitle
-% Citing examples \citeA{bost} \citeA{bry} \citeA{bob} \citeA{gre} \citeA{rosa} \citeA{duff}
+% Citing examples and the author lists
+% \citeA{bost} \citeA{bry} \citeA{bob} \citeA{gre} \citeA{rosa} \citeA{duff} \citeA{lin}
 \section{Introduction}
@@
 Formation of this paper is as it follows: \#\#, \#\#, \#\#
-%\section{A Brief History of Artificial Intelligence}
-%The preliminary work that makes AI possible dates back to the first attempts to create computers; however, these research studies were limited in theoretical knowledge until the more sophisticated hardware was developed.
-For instance, the invention of faster Central Processor Units led researchers to have more calculation power and create more detailed and elaborate algorithms \cite{bost} Alan Turing, who is regarded the one who sets the basis for AI, created a test to question a machine's ability in its intelligence \cite{gre}.
-The second milestone of AI is invention of a programming language, Lisp (list processing), in the laboratories of Massachusetts Institute of Technology.
-Even though the concepts of AI existed before Lisp, it enabled researchers to use symbolic objects rather than numbers which was a major obstacle of AI creation.
-The other issue precluding the creation of AI is the challenges of information collection.
-As mentioned above, emulation of human cognitive and perceptual process have been a major method to implement AI.
-For that reason, natural language comprehension and visual information recognition have become two main focuses in AI research.
-Another example of the imitation of humanistic features is the structure of the human brain.
-The emergence of brand new sophisticated algorithms, namely, artificial neural networks and deep learning, also show significant resemblance to neural structure of the human brain which has enabled researchers to achieve more in the creation of AI.
+
+\section{The Bigger Picture}
+\subsection{What is a Robot?}
+One common definition of AI is cited by \citeA{bost}, "A super-intelligence is any intellect that is vastly outperforms the best human brains in practically every field, including scientific creativity, general wisdom and social skills." This definition clearly distinguishes specific domain intelligent agents and AI.
+Based on this definition a computer system, Deep Blue, which is a well-known computer system for its success in chess can be considered smart within a narrow domain rather than a genuine AI supported by limitations that \citeauthor{duff} \citeyear[p.~34]{duff} speculates.\par
+
+By literary definition the term robot is derived from the Czech word "roboti" meaning serf-labor.
+However, this definition closely refering to slave-like labourer has altered to something brand new as technology advances.
+In his article entitled "The Sheer Difficulty of Defining What a Robot Is", \citeA{pear} discusses two distinctive definitions of robotics that are posed by the prominent experts in the field of robotics.
+These two definitions emphasize different aspect of robotics creating important distinctions among them.
+The first definition puts emphasis on the successful combination of a rigid body responsible for interacting with its environment and a central reasoning unit responsible for reasoning tasks based perception and cognition.
+Without a software and hardware collaboration, as \citeA{pear} cited in his article, accomplishing its tasks for a robot cannot be possible.
+The second definition, however, takes autonomy into account.
+A robot, \citeA{pear} quoted in his article, must have an detailed idea of any action formed by a tedious plan, accurate reasoning and precise action to interact with its physical environment.
+In light of these definitions, robots have to interact with its environment, which exclude any means of social interactions.
+However, \citeA{lan} asserts that socially interaction robots are significantly popular among society.
+Albeit popular, social robots, for instance a teacher robot or a guidance robot employed in an art gallery, seem to be decontextualized.
+This discrepancy brings about a major problem in individual and societal level.
+One example of this fact is that individuals have started to get strong advice from AI applications, a software crunching numbers faster than a man can do, rather than a close friend who might know better about the individual seeking advice, such as the taste in music or book.
+Even though this issue seems to have a minor flipside, once it is aggregated \citeA{lan} claims, it will create true alienation from society and confusion regarding personhood.
+In other words, roboticists have not been able  to reach a consensus on the definition of robots the embodiment of AI, \citeA{lin} noted.\par
+\subsection{What (should) does a Robot do?}
+% A strip from the old paper
+In order to make clear its obfuscated definition, the tasks of AI should be addressed.
+The task of AI is to create methods to enable machines to obtain symbolic data sets and manipulate them in order to solve generic problems in the most energy efficient and fastest fashion.
+The theory suggests that it is possible to achieve by imitating the processes of logical reasoning and decision making.
+Consequently, cognitive and perceptual systems of the human body have been scrutinized by researchers in order to emulate these processes at the hardware and software level.\par
+Along with the definitions of robotics, the applications of it extensively vary which makes it hard to define or understand the task and the responsibilities of robots.
+\citeA{lan} and \citeA{lin} listed many different applications of robotics, from labourer robots to medical purpose robots and to personal care and companion robots.
+Although \citeA{pear} excludes any means of social interaction in the definitions of robotics proposed in this article, \citeA{rodhan} exemplifies an emerging application of robotics, a molecular level robot which identifies cancerous cells and attack them by releasing antibodies, thereby eliminating cancerous cells.
+Even though, experts have not been able to solve dilemmas within the field of robotics, this steadily growing sophistication within robotics add more complex issues to the pile.
+% The reason why these social interaction dilemma matter, whether in bodily level or molecular level, is that technology advances in faster pace than that of the wisdom regarding robots and ourselves.\par
+
+\section{Conclusion}
+The notion of increasingly accelerating technology with the precious help of scientific research studies thrills individuals, and gives hope to patients.
+%However, these two prominent terms of technology closely resembles another, the Internet.
+%, otherwise yet another issue will jump into debate topics before formers could be solved. 
+Yet, it is crucially important to decide whether or not robots are simply functional machines that are utilitarian in their responsibilities and nothing more.
+If so, it is irrelevant to discuss the ethical problems arisen by its creation because the problems will become a question of accuracy of the source code that runs robots and forms AI.
+In that case, the matter should be discussed would be how to prepare individuals, societies and governments its coming.
+As for the ethical problems, they will highly likely to be no more prone to erroneousness than any other human invention.
+If evolutionary and development psychology is taken into account, the first members of fully autonomous social robots will also evolve rapidly to their excellence.
+As the expansion and the accessibility to AI and robotics increase, the prediction of the aftermath has become decrepit due to the late response of individuals and their wisdom toward these technologies.
+Thus, robotics and AI should be scrutinized to understand and formulate its definitions and functions, otherwise yet another issue will jump into debate topics before formers could be solved.
+\bibliographystyle{apacite}
+\bibliography{bibliography}
+\end{document}
 %\section{Advantages of Artificial Intelligence}
@@
 %\subsection{Solutions for the Chronic Problems of Societies}
-%\citeA{bry} claims that the common societal problems, such as the inequitable income distribution and poverty resulting from overpopulation, are impossible to cope with using regular tools and paradigms which governments now have.
+%\citeA{bry} claims that the common societal problems, such as the inequity of income distribution and poverty resulting from overpopulation, are impossible to cope with using regular tools and frameworks which governments now have.
 Having been scrutinizing social sciences, namely, developmental psychology and sociology, researchers might expand their interpretation of human behaviors which might enable them find new solutions for the given problems.
@@
 From this perspective, AI would be the best use of brain to commit what God orders \cite{gre}.
-\section{The Bigger Picture}
-\subsection{What is a Robot?}
-One common definition of AI is cited by \citeA{bost}, "A super-intelligence is any intellect that is vastly outperforms the best human brains in practically every field, including scientific creativity, general wisdom and social skills." This definition clearly distinguishes specific domain intelligent agents and AI.
-Based on this definition a computer system, Deep Blue, which is a well-known computer system for its success in chess can be considered smart within a narrow domain rather than a genuine AI supported by limitations that \citeauthor{duff} \citeyear[p.~34]{duff} speculates.\par
-
-By literary definition the term robot is derived from the Czech word "roboti" meaning serf-labor.
-However, this definition closely refering to slave-like labourer has altered to something brand new as technology advances.
-In his article entitled "The Sheer Difficulty of Defining What a Robot Is", \citeA{pear} discusses two distinctive definitions of robotics that are posed by the prominent experts in the field of robotics.
-These two definitions emphasize different aspect of robotics creating important distinctions among them.
-The first definition puts emphasis on the successful combination of a rigid body responsible for interacting with its environment and a central reasoning unit responsible for reasoning tasks based perception and cognition.
-Without s software and hardware collaboration, as \citeA{pear} cited in his article, accomplishing its tasks for a robot cannot be possible.
-The second definition, however, takes autonomy into account.
-A robot, \citeA{pear} quoted in his article, must have an detailed idea of any action formed by a tedious plan, accurate reasoning and precise action to interact with its physical environment.
-In light of these definitions, robots have to interact with its environment, which exclude any means of social interactions.
-However, \citeA{lan} asserts that socially interaction robots are significantly popular among society.
-Albeit popular, social robots, for instance a teacher robot or a guidance robot employed in an art gallery, seem to be decontextualized.
-This discrepancy brings about a major problem in individual and societal level.
-For instance, individuals have started to get strong advices from AI applications rather than a close friend who know better about the individual seeking advices, the taste of of music or book for instance, than a software crunching numbers faster than a man.
-Even though this issue seems to have a minor flipside, once it is aggregated, it will create true alienation from society and confussion regarding personhood, \citeA{lan} claims.\par
-\subsection{What (should) does a Robot do?}
-% A strip from the old paper
-In order to make clear its obfuscated definition, the tasks of AI should be addressed.
-The task of AI is to create methods to enable machines to obtain symbolic data sets and manipulate them in order to solve generic problems in the most energy efficient and fastest fashion.
-The theory suggests that it is possible to achieve by imitating the processes of logical reasoning and decision making.
-Consequently, cognitive and perceptual systems of the human body have been scrutinized by researchers in order to emulate these processes at the hardware and software level.\par
-Along with the definitions of robotics, the applications of it extensively vary which makes it hard to define or understand the task and the responsibilities of robots.
-\citeA{lan} gives different examples from a software tailored for "Jeopardy" to a teacher robot.
-Although \citeA{pear} excludes any means of social interaction in the definitions of robotics proposed in this article, \citeA{rodhan} exemplifies an emerging application of robotics, a molecular level robot which identifies cancerous cells and attach them by releasing antibodies, thereby eliminating cancerous cells.
-Even though, experts have not been able to solve dilemma within the field of robotics, this case of sophistication within robotics exemplifies another complex issue.
-The reason why these social interaction dilemma matter, whether in bodily level or molecular level, is that technology advances in faster pace that of the wisdom regarding robots and ourselves.\par
-
-\section{Conclusion}
-The notion of increasingly accelerating technology with the precious help of scientific research studies thrills individuals, and gives hope to patients.
-%However, these two prominent terms of technology closely resembles another, the Internet.
-%, otherwise yet another issue will jump into debate topics before formers could be solved. 
-Yet, it is crucially important to decide whether or not robots are simply functional machines that are utilitarian in their responsibilities and nothing more.
-If so, it is irrelevant to discuss the ethical problems arisen by its creation because the problems will become a question of accuracy of the source code that runs robots and forms AI.
-In that case, the matter should be discussed would be how to prepare individuals, societies and governments its coming.
-As for the ethical problems, they will highly likely to be no more prone to erroneousness than any other human invention.
-If evolutionary and development psychology is taken into account, the first members of fully autonomous social robots will also evolve rapidly to their excellence.
-As the expansion and the accessibility to AI and robotics increase, the prediction of the aftermath has become decrepit due to the late response of individuals and their wisdom toward these technologies.
-Thus, robotics and AI should be scrutinized to understand and formulate its definitions and functions, otherwise yet another issue will jump into debate topics before formers could be solved.
-\bibliographystyle{apacite}
-\bibliography{bibliography}
-\end{document}

### 2015-06-11 draft1.tex
Last commit before tutoring

@@
 The second definition, however, takes autonomy into account.
-A robot, \citeA{pear} quoted in his article, must have an detailed idea of any action formed by a tedious plan, accurate reasoning and precise action to interact with its physical environment.
+A robot, \citeA{pear} quoted in his article, must have an detailed idea of any action formed by a tedious plan, accurate reasoning and precise action to interact with its physical environment which closely aligns with the definition provided by \cite{lin}.
+\citeauthor{lin} \citeyear[p.~943]{lin} define a robots as "an engineered machine that senses, thinks, and acts".
 In light of these definitions, robots have to interact with its environment, which exclude any means of social interactions.
 However, \citeA{lan} asserts that socially interaction robots are significantly popular among society.
-Albeit popular, social robots, for instance a teacher robot or a guidance robot employed in an art gallery, seem to be decontextualized.
-This discrepancy brings about a major problem in individual and societal level.
+%Albeit popular, social robots, for instance a teacher robot or a guidance robot employed in an art gallery, seem to be decontextualized.
+This discrepancy brings about a major problem at individual and societal level.
 One example of this fact is that individuals have started to get strong advice from AI applications, a software crunching numbers faster than a man can do, rather than a close friend who might know better about the individual seeking advice, such as the taste in music or book.
@@
 In order to make clear its obfuscated definition, the tasks of AI should be addressed.
-The task of AI is to create methods to enable machines to obtain symbolic data sets and manipulate them in order to solve generic problems in the most energy efficient and fastest fashion.
+On the one hand,  \citeA[p.~943]{lin} noted that robots are supposedly employed in such tasks called "three D's" .\par
+%The task of AI is to create methods to enable machines to obtain symbolic data sets and manipulate them in order to solve generic problems in the most energy efficient and fastest fashion.
 The theory suggests that it is possible to achieve by imitating the processes of logical reasoning and decision making.
@@
 In that case, the matter should be discussed would be how to prepare individuals, societies and governments its coming.
+\par
 As for the ethical problems, they will highly likely to be no more prone to erroneousness than any other human invention.

### 2015-06-12 draft1.tex
Impelement all Lizzy's suggestions

@@
 \author{Murat Ambarkutuk}
-\affiliation{English Language Institute, University of Delaware \\ murata@udel.edu}
+\affiliation{English Language Institute, University of Delaware \\ murata@udel.
+edu}
 \note{First Draft; 6/8/2015; \LaTeX}
@@
  However, many researchers argue that the creation of AI will deeply change the society and it will help humankind to solve major societal problems, while others refute the arguments for the conceptual invention because of ethical problems that AI will bring such as an anticipated human annihilation by these agents.
-This paper focuses on the the ethical problems that the creation of AI will raise.}
+ This paper focuses on the the ethical problems that the creation of AI will raise.
+}
 \keywords{artificial intelligence, robotics, ethics, society} 
@@
 Thus, this paper focuses on numerous definitions for these terms and various applications of them which create intricacies and challenges in many level, varying from individual to societal level.
-Formation of this paper is as it follows: \#\#, \#\#, \#\#
+The formation of this paper is as follows: \#\#, \#\#, \#\#
 
@@
 \subsection{What is a Robot?}
-One common definition of AI is cited by \citeA{bost}, "A super-intelligence is any intellect that is vastly outperforms the best human brains in practically every field, including scientific creativity, general wisdom and social skills." This definition clearly distinguishes specific domain intelligent agents and AI.
-Based on this definition a computer system, Deep Blue, which is a well-known computer system for its success in chess can be considered smart within a narrow domain rather than a genuine AI supported by limitations that \citeauthor{duff} \citeyear[p.~34]{duff} speculates.\par
+%One common definition of AI is cited by \citeA{bost}, "A super-intelligence is any intellect that vastly outperforms the best human brains in practically every field, including scientific creativity, general %wisdom and social skills."
+%This definition clearly distinguishes specific domain intelligent agents and AI.
+% Based on this definition a computer system, Deep Blue, which is a well-known computer system for its success in chess can be considered smart within a narrow domain rather than a genuine AI supported by limitations that \citeauthor{duff} \citeyear[p.~34]{duff} speculates.
+\par
 
 By literary definition the term robot is derived from the Czech word "roboti" meaning serf-labor. 
-However, this definition closely refering to slave-like labourer has altered to something brand new as technology advances.
+However, this definition closely referring to slave-like labourer has been altered to something brand new as technology advances.
 In his article entitled "The Sheer Difficulty of Defining What a Robot Is", \citeA{pear} discusses two distinctive definitions of robotics that are posed by the prominent experts in the field of robotics.
-These two definitions emphasize different aspect of robotics creating important distinctions among them.
+These two definitions emphasize different aspects of robotics creating important distinctions among them.
 The first definition puts emphasis on the successful combination of a rigid body responsible for interacting with its environment and a central reasoning unit responsible for reasoning tasks based perception and cognition.
 Without a software and hardware collaboration, as \citeA{pear} cited in his article, accomplishing its tasks for a robot cannot be possible.
+
 The second definition, however, takes autonomy into account.
@@
 In light of these definitions, robots have to interact with its environment, which exclude any means of social interactions.
-However, \citeA{lan} asserts that socially interaction robots are significantly popular among society.
+However, \citeA{lan} asserts that socially interaction robots are significantly popular in society.
+
 %Albeit popular, social robots, for instance a teacher robot or a guidance robot employed in an art gallery, seem to be decontextualized.
-This discrepancy brings about a major problem at individual and societal level.
+
+This discrepancy brings about a major problem at the individual and societal levels.
 One example of this fact is that individuals have started to get strong advice from AI applications, a software crunching numbers faster than a man can do, rather than a close friend who might know better about the individual seeking advice, such as the taste in music or book.
 Even though this issue seems to have a minor flipside, once it is aggregated \citeA{lan} claims, it will create true alienation from society and confusion regarding personhood.
-In other words, roboticists have not been able  to reach a consensus on the definition of robots the embodiment of AI, \citeA{lin} noted.\par
+In other words, roboticists have not been able  to reach a consensus on the definition of robots the embodiment of AI, \citeA{lin} noted.
+\par
 \subsection{What (should) does a Robot do?}
@@
 In order to make clear its obfuscated definition, the tasks of AI should be addressed.
-On the one hand,  \citeA[p.~943]{lin} noted that robots are supposedly employed in such tasks called "three D's" .\par
+ On the one hand,  \citeA[p.~943]{lin} noted that robots are supposedly employed in such tasks called "three D's" .
+\par 
 %The task of AI is to create methods to enable machines to obtain symbolic data sets and manipulate them in order to solve generic problems in the most energy efficient and fastest fashion.
-The theory suggests that it is possible to achieve by imitating the processes of logical reasoning and decision making.
-Consequently, cognitive and perceptual systems of the human body have been scrutinized by researchers in order to emulate these processes at the hardware and software level.\par
+%The theory suggests that it is possible to achieve by imitating the processes of logical reasoning and decision making.
+%Consequently, cognitive and perceptual systems of the human body have been scrutinized by researchers in order to emulate these processes at the hardware and software level.
+\par
 Along with the definitions of robotics, the applications of it extensively vary which makes it hard to define or understand the task and the responsibilities of robots.
@@
 Although \citeA{pear} excludes any means of social interaction in the definitions of robotics proposed in this article, \citeA{rodhan} exemplifies an emerging application of robotics, a molecular level robot which identifies cancerous cells and attack them by releasing antibodies, thereby eliminating cancerous cells.
-Even though, experts have not been able to solve dilemmas within the field of robotics, this steadily growing sophistication within robotics add more complex issues to the pile.
-% The reason why these social interaction dilemma matter, whether in bodily level or molecular level, is that technology advances in faster pace than that of the wisdom regarding robots and ourselves.\par
+Even though experts have not been able to solve dilemmas within the field of robotics, this continuum of sophistication within robotics add more complex issues to the pile.
+
+% The reason why these social interaction dilemma matter, whether in bodily level or molecular level, is that technology advances in faster pace than that of the wisdom regarding robots and ourselves.
+\par
 
@@
 The notion of increasingly accelerating technology with the precious help of scientific research studies thrills individuals, and gives hope to patients.
-%However, these two prominent terms of technology closely resembles another, the Internet.
+
+%However, these two prominent concepts of technology closely resembles another, the Internet.
+
 %, otherwise yet another issue will jump into debate topics before formers could be solved.
+
 Yet, it is crucially important to decide whether or not robots are simply functional machines that are utilitarian in their responsibilities and nothing more.
 If so, it is irrelevant to discuss the ethical problems arisen by its creation because the problems will become a question of accuracy of the source code that runs robots and forms AI.
-In that case, the matter should be discussed would be how to prepare individuals, societies and governments its coming.
-\par
+In that case, the matter should be discussed would be how to prepare individuals, societies and governments its coming. \par
 As for the ethical problems, they will highly likely to be no more prone to erroneousness than any other human invention.
@@
  In this section, the advantages of AI are discussed.
+
 %\subsection{Solutions for the Chronic Problems of Societies}
@@
  Both authors discuss AI's advanced reasoning and interpretation underlining the new opportunities that AI might bring to societies in order to solve chronic societal problems.
+
 %\subsection{The Last Invention of Humankind That Researchers Forsee}
 %By its definition, AI appears to provide the fastest and the optimal solutions for the problems that is given which depends on supreme decision-making and cognitive processes that of humans.
-Consequently, this advanced techniques will likely to provide a privilege to have our problems solved with the help of AI.
-In other words, thanks to outstripping abilities of AI, humans might not need to invent any other tool to solve problems \cite{bost}.
+ %Consequently, this advanced techniques will likely to provide a privilege to have our problems solved with the help of AI.
+ %In other words, thanks to outstripping abilities of AI, humans might not need to invent any other tool to solve problems \cite{bost}.
+
 %\subsection{Singularity}
 %\citeA{bost} also discusses that AI might deliberately elaborate its structure and source code to enhance its abilities resulting in more advanced superintelligence, which will result in more complex structure of AI and calculation power.
+
 %\subsection{Availability of Cloning}
 %Since AI will notably rely on software implementations, it might be convenient to download its source code and promptly mount it on new hardware.
-That simplicity will likely to create more calculation power for the society and enable individuals to have personal robots.
-This possibility to create personal superintelligent agents with a cost of fractions of seconds and hardware.
+% That simplicity will likely to create more calculation power for the society and enable individuals to have personal robots.
+ %This possibility to create personal superintelligent agents with a cost of fractions of seconds and hardware.
+
 %\section{Challenges Raised by AI}
 %From the very beginning of the conceptual designs of AI, it has been the most debated issue in the engineering and scientific societies due to its ethical problems.
-Near future is fecund to a dilemma which humankind will face in AI's moral integrity and its position in society \cite{duff}.
-This section synthesizes the ethical issues and counterarguments coping with them.
+% Near future is fecund to a dilemma which humankind will face in AI's moral integrity and its position in society \cite{duff}.
+% This section synthesizes the ethical issues and counterarguments coping with them.
+
 %\subsection{Security Issues}
 %Since robots can be regarded self-conscience agents, thanks to advanced reasoning, cognitive and perceptual abilities provided by AI, a major issue having been discussed is whether or not military, one of the biggest supporter of AI, is being sincere with its funding \cite{gre}.
-Of the many supporters of AI, military appears to be the most questionable one due to plausible intentions of creation of humanoid army.
-The ultimate reason of AI which is elevation of life conditions and inquiry for the chronic problems of our societies notwithstanding, utilization of weaponized robotic army would increment the vast possession of ammunition and weaponization problem rather than solving our problems.\par
-%Although being able to elaborate its source code by itself and being easily cloned are the factors considered advantage for the society, \citeA{duff} claims that combination of these factors would make AI able to easily reproduce itself, which means robots may own robots that they create in the long term.
-Consequently, second generations robots created by the first generations would be utterly dependent on the first generation robots which means the first generation robots might command their offspring how ever they want.
-This unpredictable action-decision chain raises a major security problems including human annihilation for the society.
+% Of the many supporters of AI, military appears to be the most questionable one due to plausible intentions of creation of humanoid army.
+%The ultimate reason of AI which is elevation of life conditions and inquiry for the chronic problems of our societies notwithstanding, utilization of weaponized robotic army would increment the vast possession of ammunition and weaponization problem rather than solving our problems.
+% \par
+%Although being able to elaborate its source code by itself and being easily cloned are the factors considered advantage for the society, \citeA{duff} claims that combination of these factors would % make AI able to easily reproduce itself, which means robots may own robots that they create in the long term.
+% Consequently, second generations robots created by the first generations would be utterly dependent on the first generation robots which means the first generation robots might command their offspring how ever they want.
+% This unpredictable action-decision chain raises a major security problems including human annihilation for the society.
+ %
 %\subsection{Socio-economic Issues}
 %The rise of computers which has led the employment of robots in industry lessen the human employment starting from late 70's.
-Because of the downsizing tendency of corporation which resulted from this replacement, millions of low-skilled workers lost their jobs.
-Given that fact, \citeA{gre} predicts the aftermath of the creation of AI.
-This vast computation power might replace most of the low-skilled laborers with the more powerful robots.
-In the light of that prediction, highly developed economies may show an extensive recession.\par
+% Because of the downsizing tendency of corporation which resulted from this replacement, millions of low-skilled workers lost their jobs.
+ %Given that fact, \citeA{gre} predicts the aftermath of the creation of AI.
+ %This vast computation power might replace most of the low-skilled laborers with the more powerful robots.
+ %In the light of that prediction, highly developed economies may show an extensive recession.
+%\par
 %Along with the economical effects of workplace computerization, eradication of low-skilled jobs may lead the expansion of the gap among the social groups.
-For instance, those who can use computers or know develop software have reached to higher classes in the societies.
-This expansion of gap among the social groups contradicts the societal goals of the creation of AI.\par
+ %For instance, those who can use computers or know develop software have reached to higher classes in the societies.
+ %This expansion of gap among the social groups contradicts the societal goals of the creation of AI.
+%\par
 %In addition to former arguments, \citeA{rosa} proposes yet another.
-Even though researchers, for instance, want to create a narrow-domain savvy robot, the robot may want to change its profession from the one that it had been taught or coded to a brand new one.
-This probable change of profession contradicts with the reason its creation purpose which may be interpreted as a act of disobey to its master.
+ %Even though researchers, for instance, want to create a narrow-domain savvy robot, the robot may want to change its profession from the one that it had been taught or coded to a brand new one.
+ %This probable change of profession contradicts with the reason its creation purpose which may be interpreted as a act of disobey to its master.
+
 %\subsection{Legal Issues}
 %Since self-awareness of AI, it can be regarded as an independent agent.
-This conceptual independency, however, raises a ethical dilemma.
-Many researchers has been questioning whether or not superintelligent agents have duties to the society and to what extent governments give social rights \cite{bob}.
-Given that approach, \cite{kerb} mentions early speculations of social equality regarding civil and political rights among robots and humans in Japanese anime and mangas which artworks are consisted of futuristic plots including robots cohabitating and interacting with humans.
-These questions caused by the legal ramification of AI.
-\citeA{gre} discusses that it is not obvious that who will be responsible for results of AI's actions.
-Not only does AI's position in the society matter, but it is also equally important for governments to decide the AI's responsibility for the society, vice versa.
-\par
+ %This conceptual independency, however, raises a ethical dilemma.
+% Many researchers has been questioning whether or not superintelligent agents have duties to the society and to what extent governments give social rights \cite{bob}.
+ %Given that approach, \cite{kerb} mentions early speculations of social equality regarding civil and political rights among robots and humans in Japanese anime and mangas which artworks are %consisted of futuristic plots including robots cohabitating and interacting with humans.
+ %These questions caused by the legal ramification of AI.
+ %\citeA{gre} discusses that it is not obvious that who will be responsible for results of AI's actions.
+% Not only does AI's position in the society matter, but it is also equally important for governments to decide the AI's responsibility for the society, vice versa.
+% \par
 %The counterargument was proposed by \citeA{rosa} by underlining the evolutionary approach on human morality.
-As \citeA{rosa} cited, probability of error in evolution of human morality and nature displays a significant resemblance to the errors that might AI commit.
-For that reason, it is more logical to create a ground that can tolerate the probable AI's errors.
+ %As \citeA{rosa} cited, probability of error in evolution of human morality and nature displays a significant resemblance to the errors that might AI commit.
+ %For that reason, it is more logical to create a ground that can tolerate the probable AI's errors.
+
 %\subsection{Religious Issues}
 %One issue that discussed among scholars is whether or not creating a self-aware machine which is able to reason in the same level with human intelligence would be stealing the role of God.
-In addition to that issue, almost all of the monotheistic religions put significant emphasis on the features of God concept.
-According to these religions, God himself is unique and incomparably exceptional than the ones what he created.
-Of the many major sins, imitating God, or in other words one's God-like manifestation, is the unforgivable one.\citeA{gre} discusses this issue by showing the similarities of creation of a self-aware agent and creation concept of God.
-Moreover, \citeA{duff} mentions human-like form that researchers tend to build social robots, an example of embodiment of AI.
-In the light of these facts, the concept of God and the creation of AI seems to intersect to some extent.\par
+ %In addition to that issue, almost all of the monotheistic religions put significant emphasis on the features of God concept.
+ %According to these religions, God himself is unique and incomparably exceptional than the ones what he created.
+ %Of the many major sins, imitating God, or in other words one's God-like manifestation, is the unforgivable one.
+%\citeA{gre} discusses this issue by showing the similarities of creation of a self-aware agent and creation concept of God.
+ %Moreover, \citeA{duff} mentions human-like form that researchers tend to build social robots, an example of embodiment of AI.
+ %In the light of these facts, the concept of God and the creation of AI seems to intersect to some extent.
+%\par
 %The counterarguments put significance on more God and abilities that humans given by him rather than the limitations provided by the rules of religions.
-This approach to research and development of AI considers human and nature the masterpiece of God.
-For instance, brain is one the biggest resource that provided by God in order to make humans able to create tools and techniques to solve their problems, namely, taming the nature, building societies and elevating one's position in these societies.
-From this perspective, AI would be the best use of brain to commit what God orders \cite{gre}.
+% This approach to research and development of AI considers human and nature the masterpiece of God.
+% For instance, brain is one the biggest resource that provided by God in order to make humans able to create tools and techniques to solve their problems, namely, taming the nature, building societies and elevating one's position in these societies.
+ %From this perspective, AI would be the best use of brain to commit what God orders \cite{gre}.

### 2015-06-12 draft1.tex
Seperate new sentences with line breaks

@@
 Sometimes, solutions for any arbitrary problem can be solved by seeing the bigger picture rather than scrutinizing tiny details.
-Thus, this paper focuses on numerous definitions for these terms and various applications of them which create intricacies and challenges in many level, varying from individual to societal level.
+Thus, this paper focuses on numerous definitions for these concepts and their various applications which create intricacies and challenges in many level, varying from individual to societal level.
 The formation of this paper is as follows: \#\#, \#\#, \#\#

### 2015-06-12 draft1.tex
Commit for Isil

@@
 \maketitle
-% Citing examples and the author lists
-% \citeA{bost} \citeA{bry} \citeA{bob} \citeA{gre} \citeA{rosa} \citeA{duff} \citeA{lin}
+
 \section{Introduction}
@@
 Thus, this paper focuses on numerous definitions for these concepts and their various applications which create intricacies and challenges in many level, varying from individual to societal level.
-The formation of this paper is as follows: \#\#, \#\#, \#\#
+The formation of this paper is as follows: First section will emphasize on the issues that robotics have arisen; the second and third section then scrutinize the definitions and applications of robots; respectively in order to locate the roots of these issues and intricacies.
+
+\section{The Most Profound Issues of Robotics}
+From the very beginning of the conceptual designs of AI, it has been the most debated issue in the engineering and scientific societies due to its ethical problems.
+Near future is fecund to a dilemma which humankind will face in AI's moral integrity and its position in society.
+This section synthesizes the issues risen by the creation of AI and employment robots in a wide spectrum of tasks.
+
+\subsection{Safety Issues}
+% Since robots can be regarded self-conscience agents, thanks to advanced reasoning, cognitive and perceptual abilities provided by AI, 
+A major issue having been discussed is whether or not military, one of the biggest supporter of robotics, is being sincere with its funding purposes \cite{gre}.
+Of the many supporters of such research studies, military appears to be the most questionable one due to plausible intentions of creation of humanoid army.
+The ultimate reason of robots which is elevation of life conditions and inquiry for applicable solutions for the chronic problems of our societies, by the nature of any given tools that invented by humankind, notwithstanding, utilization of weaponized robotic army would increment the vast possession of ammunition and weaponization problem rather than solving chronic problems of relationships among governments.
+The probable mass employment of battlefield robots is one of the biggest concern when it comes to mediate a inter-governmental conflict.
+Such probability may put countries in circumstances which closely resembles to the Cold War.
+\par
+
+\subsection{Legal and Ethical Issues}
+Robots are envisioned to be controlled by a such intelligence which enable their to perceive their surrounding environments where they interact with the objects.
+Thus, they can be regarded as independent agents.
+This conceptual independency, however, raises an ethical dilemma caused by the absence of legal ramification of AI.
+Many researchers has been questioning whether or not these super-intelligent agents should have duties to the society and to what extent governments give social rights \cite{bob}.
+Given that approach, \cite{kerb} mentions early speculations of social equality regarding civil and political rights among robots and humans in Japanese anime and mangas which artworks are %consisted of futuristic plots including robots cohabitating and interacting with humans.
+\citeA{gre} discusses that it is not obvious that who will be responsible for results of AI's actions.
+Not only does AI's position in the society matter, but it is also equally important for governments to decide the AI's responsibility for the society, vice versa. \par
+
+\subsection{Socio-economic Issues}
+The rise of computers which has led the employment of robots in industry lessen the human employment starting from late 70's.
+Because of the downsizing tendency of corporation which resulted from this replacement, millions of low-skilled workers lost their jobs.
+Given that fact, \citeA{gre} predicts the aftermath of the creation of AI.
+This vast computation power might replace most of the low-skilled laborers with the more powerful robots.
+In the light of that prediction, highly developed economies may show an extensive recession. \par
+Along with the economical effects of workplace computerization, eradication of low-skilled jobs may lead the expansion of the gap among the social groups.
+For instance, those who can use computers or know develop software have reached to higher classes in the societies.
+This expansion of gap among the social groups contradicts the societal goals of the creation of AI. \par
+In addition to former arguments, \citeA{rosa} proposes yet another.
+Even though researchers, for instance, want to create a narrow-domain savvy robot, the robot may want to change its profession from the one that it had been taught or coded to a brand new one.
+This probable change of profession contradicts with the reason its creation purpose which may be interpreted as a act of disobey to its master.
 
 \section{The Bigger Picture}
+
 \subsection{What is a Robot?}
@@
 The first definition puts emphasis on the successful combination of a rigid body responsible for interacting with its environment and a central reasoning unit responsible for reasoning tasks based perception and cognition.
-Without a software and hardware collaboration, as \citeA{pear} cited in his article, accomplishing its tasks for a robot cannot be possible.
+Without a software and hardware collaboration, as \citeA{pear} cites in his article, accomplishing its tasks for a robot cannot be possible.
 
 The second definition, however, takes autonomy into account.
-A robot, \citeA{pear} quoted in his article, must have an detailed idea of any action formed by a tedious plan, accurate reasoning and precise action to interact with its physical environment which closely aligns with the definition provided by \cite{lin}.
+A robot, \citeA{pear} quotes in his article, must have an detailed idea of any action formed by a tedious plan, accurate reasoning and precise action to interact with its physical environment which closely aligns with the definition provided by \cite{lin}.
 \citeauthor{lin} \citeyear[p.~943]{lin} define a robots as "an engineered machine that senses, thinks, and acts".
@@
 \par
+
 \subsection{What (should) does a Robot do?}
 % A strip from the old paper
-In order to make clear its obfuscated definition, the tasks of AI should be addressed.
- On the one hand,  \citeA[p.~943]{lin} noted that robots are supposedly employed in such tasks called "three D's" .
+In order to make its obfuscated definition clear, the tasks of AI should be addressed.
+On the one hand,  \citeA[p.~943]{lin} note that robots are supposedly employed in such tasks called "three D's" referring "dull, dirty, or dangerous" tasks.
+From that instruction, a robot should replace human where the task contains either mundane chores, or risks of contamination, or threatening factors for human lives.
 \par 
@@
 \par
-Along with the definitions of robotics, the applications of it extensively vary which makes it hard to define or understand the task and the responsibilities of robots.
-\citeA{lan} and \citeA{lin} listed many different applications of robotics, from labourer robots to medical purpose robots and to personal care and companion robots.
-Although \citeA{pear} excludes any means of social interaction in the definitions of robotics proposed in this article, \citeA{rodhan} exemplifies an emerging application of robotics, a molecular level robot which identifies cancerous cells and attack them by releasing antibodies, thereby eliminating cancerous cells.
+%Along with the definitions of robotics, the applications of it extensively vary which makes it hard to define or understand the task and the responsibilities of robots.
+On the other hand, \citeA{lan} and \citeA{lin} list many different real life robotic applications, from labourer robots to medical purpose robots and to personal care and companion robots, which contradicts with given instruction.
+While \citeA{pear} also excludes any means of social interaction in the definitions of robotics proposed in this article, \citeA{rodhan} elaborates this issue by indicating an emerging application of robotics, a molecular level robot which identifies cancerous cells and attack them by releasing antibodies, thereby eliminating cancerous cells.
 Even though experts have not been able to solve dilemmas within the field of robotics, this continuum of sophistication within robotics add more complex issues to the pile.
@@
 The notion of increasingly accelerating technology with the precious help of scientific research studies thrills individuals, and gives hope to patients.
-
 %However, these two prominent concepts of technology closely resembles another, the Internet.
-
 %, otherwise yet another issue will jump into debate topics before formers could be solved.
-
 Yet, it is crucially important to decide whether or not robots are simply functional machines that are utilitarian in their responsibilities and nothing more.
@@
 \end{document}
-%\section{Advantages of Artificial Intelligence}
-%Anthropomorphism is the basis of AI which is the imitation of the way that humans find solutions for problems.
- As a result of this imitation process, anticipated outcomes are not only solving the problem itself, but also finding the optimal solution for the problem in shortest time period possible.
- This speed and ability to solve problems will be advantageous for humankind.
- In this section, the advantages of AI are discussed.
-
-%\subsection{Solutions for the Chronic Problems of Societies}
-%\citeA{bry} claims that the common societal problems, such as the inequity of income distribution and poverty resulting from overpopulation, are impossible to cope with using regular tools and frameworks which governments now have.
- Having been scrutinizing social sciences, namely, developmental psychology and sociology, researchers might expand their interpretation of human behaviors which might enable them find new solutions for the given problems.
- Moreover, elimination of aging and eradication of diseases might be the possible consequence of the creation of AI \citeA{bost}.
- Both authors discuss AI's advanced reasoning and interpretation underlining the new opportunities that AI might bring to societies in order to solve chronic societal problems.
-
-%\subsection{The Last Invention of Humankind That Researchers Forsee}
-%By its definition, AI appears to provide the fastest and the optimal solutions for the problems that is given which depends on supreme decision-making and cognitive processes that of humans.
- %Consequently, this advanced techniques will likely to provide a privilege to have our problems solved with the help of AI.
- %In other words, thanks to outstripping abilities of AI, humans might not need to invent any other tool to solve problems \cite{bost}.
-
-%\subsection{Singularity}
-%\citeA{bost} also discusses that AI might deliberately elaborate its structure and source code to enhance its abilities resulting in more advanced superintelligence, which will result in more complex structure of AI and calculation power.
-
-%\subsection{Availability of Cloning}
-%Since AI will notably rely on software implementations, it might be convenient to download its source code and promptly mount it on new hardware.
-% That simplicity will likely to create more calculation power for the society and enable individuals to have personal robots.
- %This possibility to create personal superintelligent agents with a cost of fractions of seconds and hardware.
-
-%\section{Challenges Raised by AI}
-%From the very beginning of the conceptual designs of AI, it has been the most debated issue in the engineering and scientific societies due to its ethical problems.
-% Near future is fecund to a dilemma which humankind will face in AI's moral integrity and its position in society \cite{duff}.
-% This section synthesizes the ethical issues and counterarguments coping with them.
-
-%\subsection{Security Issues}
-%Since robots can be regarded self-conscience agents, thanks to advanced reasoning, cognitive and perceptual abilities provided by AI, a major issue having been discussed is whether or not military, one of the biggest supporter of AI, is being sincere with its funding \cite{gre}.
-% Of the many supporters of AI, military appears to be the most questionable one due to plausible intentions of creation of humanoid army.
-%The ultimate reason of AI which is elevation of life conditions and inquiry for the chronic problems of our societies notwithstanding, utilization of weaponized robotic army would increment the vast possession of ammunition and weaponization problem rather than solving our problems.
-% \par
-%Although being able to elaborate its source code by itself and being easily cloned are the factors considered advantage for the society, \citeA{duff} claims that combination of these factors would % make AI able to easily reproduce itself, which means robots may own robots that they create in the long term.
-% Consequently, second generations robots created by the first generations would be utterly dependent on the first generation robots which means the first generation robots might command their offspring how ever they want.
-% This unpredictable action-decision chain raises a major security problems including human annihilation for the society.
- %
-%\subsection{Socio-economic Issues}
-%The rise of computers which has led the employment of robots in industry lessen the human employment starting from late 70's.
-% Because of the downsizing tendency of corporation which resulted from this replacement, millions of low-skilled workers lost their jobs.
- %Given that fact, \citeA{gre} predicts the aftermath of the creation of AI.
- %This vast computation power might replace most of the low-skilled laborers with the more powerful robots.
- %In the light of that prediction, highly developed economies may show an extensive recession.
-%\par
-%Along with the economical effects of workplace computerization, eradication of low-skilled jobs may lead the expansion of the gap among the social groups.
- %For instance, those who can use computers or know develop software have reached to higher classes in the societies.
- %This expansion of gap among the social groups contradicts the societal goals of the creation of AI.
-%\par
-%In addition to former arguments, \citeA{rosa} proposes yet another.
- %Even though researchers, for instance, want to create a narrow-domain savvy robot, the robot may want to change its profession from the one that it had been taught or coded to a brand new one.
- %This probable change of profession contradicts with the reason its creation purpose which may be interpreted as a act of disobey to its master.
-
-%\subsection{Legal Issues}
-%Since self-awareness of AI, it can be regarded as an independent agent.
- %This conceptual independency, however, raises a ethical dilemma.
-% Many researchers has been questioning whether or not superintelligent agents have duties to the society and to what extent governments give social rights \cite{bob}.
- %Given that approach, \cite{kerb} mentions early speculations of social equality regarding civil and political rights among robots and humans in Japanese anime and mangas which artworks are %consisted of futuristic plots including robots cohabitating and interacting with humans.
- %These questions caused by the legal ramification of AI.
- %\citeA{gre} discusses that it is not obvious that who will be responsible for results of AI's actions.
-% Not only does AI's position in the society matter, but it is also equally important for governments to decide the AI's responsibility for the society, vice versa.
-% \par
-%The counterargument was proposed by \citeA{rosa} by underlining the evolutionary approach on human morality.
- %As \citeA{rosa} cited, probability of error in evolution of human morality and nature displays a significant resemblance to the errors that might AI commit.
- %For that reason, it is more logical to create a ground that can tolerate the probable AI's errors.
-
-%\subsection{Religious Issues}
-%One issue that discussed among scholars is whether or not creating a self-aware machine which is able to reason in the same level with human intelligence would be stealing the role of God.
- %In addition to that issue, almost all of the monotheistic religions put significant emphasis on the features of God concept.
- %According to these religions, God himself is unique and incomparably exceptional than the ones what he created.
- %Of the many major sins, imitating God, or in other words one's God-like manifestation, is the unforgivable one.
-%\citeA{gre} discusses this issue by showing the similarities of creation of a self-aware agent and creation concept of God.
- %Moreover, \citeA{duff} mentions human-like form that researchers tend to build social robots, an example of embodiment of AI.
- %In the light of these facts, the concept of God and the creation of AI seems to intersect to some extent.
-%\par
-%The counterarguments put significance on more God and abilities that humans given by him rather than the limitations provided by the rules of religions.
-% This approach to research and development of AI considers human and nature the masterpiece of God.
-% For instance, brain is one the biggest resource that provided by God in order to make humans able to create tools and techniques to solve their problems, namely, taming the nature, building societies and elevating one's position in these societies.
- %From this perspective, AI would be the best use of brain to commit what God orders \cite{gre}.

### 2015-06-12 draft1.tex
Commit unknown changes

@@
 \citeA{gre} discusses that it is not obvious that who will be responsible for results of AI's actions.
-Not only does AI's position in the society matter, but it is also equally important for governments to decide the AI's responsibility for the society, vice versa. \par
+Not only does AI's position in the society matter, but it is also equally important for governments to decide the AI's responsibility for the society, vice versa.
 
@@
 The rise of computers which has led the employment of robots in industry lessen the human employment starting from late 70's.
-Because of the downsizing tendency of corporation which resulted from this replacement, millions of low-skilled workers lost their jobs.
+Because of the downsizing tendency of corporations which resulted from this replacement, millions of low-skilled workers lost their jobs.
 Given that fact, \citeA{gre} predicts the aftermath of the creation of AI.
-This vast computation power might replace most of the low-skilled laborers with the more powerful robots.
+This vast computation power might replace most of the low-skilled labourers with the more powerful robots.
 In the light of that prediction, highly developed economies may show an extensive recession. \par
@@
 \section{The Bigger Picture}
-
 \subsection{What is a Robot?}
@@
 Even though experts have not been able to solve dilemmas within the field of robotics, this continuum of sophistication within robotics add more complex issues to the pile.
-
 % The reason why these social interaction dilemma matter, whether in bodily level or molecular level, is that technology advances in faster pace than that of the wisdom regarding robots and ourselves.

### 2015-06-13 draft1.tex
Edit abstract

@@
  Since the rise of the computers, Artificial Intelligence (AI) has been one of the most debated issues in the field of engineering.
- Research toward the creation of AI includes a creation of self-aware machines that have superior intellectual abilities to that of human abilities.
- However, many researchers argue that the creation of AI will deeply change the society and it will help humankind to solve major societal problems, while others refute the arguments for the conceptual invention because of ethical problems that AI will bring such as an anticipated human annihilation by these agents.
- This paper focuses on the the ethical problems that the creation of AI will raise.
+ Research toward robotics is also based upon the creation of AI that will run the robots thanks to superior cognitive and perceptive abilities of AI than that of man. 
+ However, many researchers argue that the creation of AI will deeply elevate society and it will help humankind to solve major societal problems, while others refute the arguments for that conceptual invention because of ethical problems that AI will bring.
+ This paper explores the ethical problems that the creation of AI will raise, and it attribute these problems resulted from widely varying definitons and the applications of these .
 }
@@
 \section{Introduction}
-Even though the term robot was coined two centuries ago and the idea of AI emerged decades ago, some of the problems that have been raised by these two terms are yet to be solved.
+Even though the term robot was coined two centuries ago and the idea of Artificial Intelligence (AI) emerged decades ago, some of the problems that have been raised by these two terms are yet to be solved.
 Sometimes, solutions for any arbitrary problem can be solved by seeing the bigger picture rather than scrutinizing tiny details.

### 2015-06-13 draft1.tex
Fix typo in the abstract

@@
  However, many researchers argue that the creation of AI will deeply elevate society and it will help humankind to solve major societal problems, while others refute the arguments for that conceptual invention because of ethical problems that AI will bring.
- This paper explores the ethical problems that the creation of AI will raise, and it attribute these problems resulted from widely varying definitons and the applications of these .
+ This paper explores the ethical problems that the creation of AI will raise, and it attributes these problems to widely varying definitions and the applications of these technologies.
 }

### 2015-06-13 draft1.tex
Add .gitignore file

@@
  Since the rise of the computers, Artificial Intelligence (AI) has been one of the most debated issues in the field of engineering.
- Research toward robotics is also based upon the creation of AI that will run the robots thanks to superior cognitive and perceptive abilities of AI than that of man. 
+ Robots are also subject to these debates because that tangible spin-off technology that will be run by such an AI that will have superior cognitive and perceptive abilities than that of man. 
  However, many researchers argue that the creation of AI will deeply elevate society and it will help humankind to solve major societal problems, while others refute the arguments for that conceptual invention because of ethical problems that AI will bring.

### 2015-06-13 draft1.tex
Edit the Introduction section

@@
 Robots are also subject to these debates because that tangible spin-off technology that will be run by such an AI that will have superior cognitive and perceptive abilities than that of man. 
- However, many researchers argue that the creation of AI will deeply elevate society and it will help humankind to solve major societal problems, while others refute the arguments for that conceptual invention because of ethical problems that AI will bring.
- This paper explores the ethical problems that the creation of AI will raise, and it attributes these problems to widely varying definitions and the applications of these technologies.
+Many researchers argue that the creation of AI will deeply elevate society and it will help humankind to solve major societal problems, while others refute the arguments for that conceptual invention.
+This paper explores these issues that the creation of AI will raise, and it attributes these problems to widely varying definitions and the applications of these technologies.
 }
@@
 \section{Introduction}
-Even though the term robot was coined two centuries ago and the idea of Artificial Intelligence (AI) emerged decades ago, some of the problems that have been raised by these two terms are yet to be solved.
-Sometimes, solutions for any arbitrary problem can be solved by seeing the bigger picture rather than scrutinizing tiny details.
-Thus, this paper focuses on numerous definitions for these concepts and their various applications which create intricacies and challenges in many level, varying from individual to societal level.
-The formation of this paper is as follows: First section will emphasize on the issues that robotics have arisen; the second and third section then scrutinize the definitions and applications of robots; respectively in order to locate the roots of these issues and intricacies.
+Even though the term robot was coined two centuries ago and preliminary contemplation of Artificial Intelligence (AI) emerged decades ago, some of the problems that have been raised by these two terms are yet to be solved.
+Sometimes, solutions for any arbitrary problem can be addressed by seeing the bigger picture rather than scrutinizing tiny details.
+Thus, this paper explores these problems and then analyzes the numerous definitions and applications of these technologies which pose challenges on varying levels, from individual to societal.
+The formation of this paper is as follows: The first section categorizes the issues that robotics have arisen; the second and third sections then scrutinize the definitions and the applications of robots, respectively, to attribute the reasons of these issues.
 

### 2015-06-13 draft1.tex
Edit 'The Most Profound Issues of Robotics' section

@@
 \section{The Most Profound Issues of Robotics}
-From the very beginning of the conceptual designs of AI, it has been the most debated issue in the engineering and scientific societies due to its ethical problems.
-Near future is fecund to a dilemma which humankind will face in AI's moral integrity and its position in society.
-This section synthesizes the issues risen by the creation of AI and employment robots in a wide spectrum of tasks.
+From the very early contemplations of AI, it has been the most controversial issue within the engineering and scientific societies due to its ethical problems.
+Near future is fecund to many dilemmas which humankind, soon or later, will face regarding AI's moral integrity and its position in society.
+This section synthesizes the issues of employment of AI and robots in a wide spectrum of tasks.
 

### 2015-06-13 draft1.tex
Edit Safety Issues section

@@
 % Since robots can be regarded self-conscience agents, thanks to advanced reasoning, cognitive and perceptual abilities provided by AI, 
-A major issue having been discussed is whether or not military, one of the biggest supporter of robotics, is being sincere with its funding purposes \cite{gre}.
+Akin to the nature of any given invention, the ultimate reason for the invention of robots is the elevation of life conditions and inquiry for applicable solutions for problems of societies.
+However, a major issue having been discussed is whether or not military, one of the biggest supporter of robotics, is being sincere with its funding purposes \cite{gre}.
 Of the many supporters of such research studies, military appears to be the most questionable one due to plausible intentions of creation of humanoid army.
-The ultimate reason of robots which is elevation of life conditions and inquiry for applicable solutions for the chronic problems of our societies, by the nature of any given tools that invented by humankind, notwithstanding, utilization of weaponized robotic army would increment the vast possession of ammunition and weaponization problem rather than solving chronic problems of relationships among governments.
-The probable mass employment of battlefield robots is one of the biggest concern when it comes to mediate a inter-governmental conflict.
-Such probability may put countries in circumstances which closely resembles to the Cold War.
+% <readagain>
+This utilization of a weaponized robotic army would boost the vast possession of ammunition problem instead of mediating inter-governmental conflicts.
+% </readagain>
+This contentious utilization of battlefield robots is one of the biggest concern when it comes to mediate inter-governmental conflicts.
+Such probability may put countries in circumstances resembling strongly to the Cold War.
 \par
+
+% Add Hacking Section
+
+% Add human proneness to fail and errors in source code. (skepticism and uncanny)
 

### 2015-06-13 draft1.tex
Edit the Legal and Ethical Issues section

@@
 \subsection{Legal and Ethical Issues}
-Robots are envisioned to be controlled by a such intelligence which enable their to perceive their surrounding environments where they interact with the objects.
+Robots are envisioned to be controlled by a such intelligence which enable their to perceive their surrounding environments where they interact with the objects by themselves.
 Thus, they can be regarded as independent agents.
-This conceptual independency, however, raises an ethical dilemma caused by the absence of legal ramification of AI.
-Many researchers has been questioning whether or not these super-intelligent agents should have duties to the society and to what extent governments give social rights \cite{bob}.
-Given that approach, \cite{kerb} mentions early speculations of social equality regarding civil and political rights among robots and humans in Japanese anime and mangas which artworks are %consisted of futuristic plots including robots cohabitating and interacting with humans.
-\citeA{gre} discusses that it is not obvious that who will be responsible for results of AI's actions.
-Not only does AI's position in the society matter, but it is also equally important for governments to decide the AI's responsibility for the society, vice versa.
+This conceptual freedom, however, raises an ethical dilemma caused by the absence of legal ramifications of AI.
+\citeA{gre} examine that ambiguity by posing a controversial question: "Who will be responsible for results of AI's actions and failure?"
+Since the contemplation of AI and robots indicates that robots will supposedly make their own choices take actions according to these choices, another interesting question arises: "Would robots be prosecuted -maybe executed- because of the fails they commit?"
+Similar to the questions above, there are many questions that governments need to address by creating regulations and laws under which robots will be positioned. \par
+Furthermore, many researchers has been questioning whether or not these super-intelligent agents should have duties to society; if so, to what extent governments should give social rights to robots.
+\citeA{bob} addresses this issue by underlining basic rights and duties of citizens such as taxing and voting.
+In other words, not only does AI's legal ramification matter, but it is also equally important for governments to decide the AI's responsibility for the society, vice versa.
+To address this issue, \citeA{kerb} analyzes Japanese artworks showing futuristic plots based upon robots cohabitating and interacting with humans.
+These artworks depicts the very early speculations of social equality between man and machine regarding civil and political rights among.
+Kerb's evaluation of these artworks concludes that robots, depicted and envisioned in the artworks, are neither overlords nor serf-laborers.
 
@@
 In the light of that prediction, highly developed economies may show an extensive recession. \par
+
 Along with the economical effects of workplace computerization, eradication of low-skilled jobs may lead the expansion of the gap among the social groups.
@@
 This expansion of gap among the social groups contradicts the societal goals of the creation of AI. \par
-In addition to former arguments, \citeA{rosa} proposes yet another.
-Even though researchers, for instance, want to create a narrow-domain savvy robot, the robot may want to change its profession from the one that it had been taught or coded to a brand new one.
-This probable change of profession contradicts with the reason its creation purpose which may be interpreted as a act of disobey to its master.
+
+% Personal robots personhood problem.
 
@@
 Even though this issue seems to have a minor flipside, once it is aggregated \citeA{lan} claims, it will create true alienation from society and confusion regarding personhood.
-In other words, roboticists have not been able  to reach a consensus on the definition of robots the embodiment of AI, \citeA{lin} noted.
+In other words, roboticists have not been able  to reach a consensus on the definition of robots the embodiment of AI, \citeA{lin} note.
 \par

### 2015-06-13 draft1.tex
Change one section title to "Psychological Challenges and Socio-economic Issues" Edit section "Psychological Challenges and Socio-economic Issues"

@@
 
-\subsection{Socio-economic Issues}
-The rise of computers which has led the employment of robots in industry lessen the human employment starting from late 70's.
+\subsection{Psychological Challenges and Socio-economic Issues}
+Social interaction is what differentiates humans from machines.
+However, as the research studies toward creation of AI have gone deeper, robots have become more socially interactive within society.
+For instance, before GPS became publicly available, route planning was based upon map-reading and asking directions of the locals.
+In light of this example, AI has become route planning assistant and has decreased the interrelation among individuals.
+According to \citeA{lan}, reformation of our perception towards AI poses misconceptions regarding personhood and promotes loneliness.
+This issue truly matters due to the fact that alienation from the society relies on that misconception.
+Another matter that deeply affects human psychology is that innovative superiority of robots seems to increase profitability and efficiency, albeit undermining the true value of failures.
+Given that failures are one of most essential component of human learning process, superiority of AI discourage individuals to commit any form of actions due to fear of failures. 
+This fear impedes the same body of individuals to learn and trust human judgment, hindering them completely.
+Depression and other similar psychological challenges are the most profound indicators of the aftermaths of inaccurate definition of AI. \par
+
+Furthermore, the rise of computers has led to lessen the human employment starting from late 70's.
 Because of the downsizing tendency of corporations which resulted from this replacement, millions of low-skilled workers lost their jobs.
-Given that fact, \citeA{gre} predicts the aftermath of the creation of AI.
-This vast computation power might replace most of the low-skilled labourers with the more powerful robots.
-In the light of that prediction, highly developed economies may show an extensive recession. \par
+Robots and AI supposedly represent the maxima of accuracy and repeatability which promotes reliance on AI thanks to their cognitive and learning abilities that outperform human abilities.
+Given that historic fact, \citeA{gre} predict that this reliance might cause an inevitable replacement of low-skilled laborers with the more powerful robots, akin to aftermaths of the computerization era.
+In light of that prediction, highly developed economies may show a strong recession due to the significant lost in human work power and if this aggressive expansion continues, other occupations and professions will be under the same risk of mechanization.
+\par
 
-Along with the economical effects of workplace computerization, eradication of low-skilled jobs may lead the expansion of the gap among the social groups.
-For instance, those who can use computers or know develop software have reached to higher classes in the societies.
-This expansion of gap among the social groups contradicts the societal goals of the creation of AI. \par
-
-% Personal robots personhood problem.
+Along with the economical effects of workplace computerization, eradication of low-skilled jobs may lead the expansion of the gap among the social groups \cite{gre}.
+For instance, as the first paragraph of this section indicates, those who can use computers or know developing software have reached to higher classes in societies, while other could not seize the same momentum.
+This computerization instruct young individual belong to lower layers of society to believe that there is no way to elevate in society.
+This expansion in the gap with in society and among the social groups clearly contradicts to the societal goals of robotics.
 
@@
 If so, it is irrelevant to discuss the ethical problems arisen by its creation because the problems will become a question of accuracy of the source code that runs robots and forms AI.
-In that case, the matter should be discussed would be how to prepare individuals, societies and governments its coming. \par
+In that case, the matter should be discussed would be how to mitigate, even eradicate, human errors taking place when roboticists develop robots and AI. \par
 As for the ethical problems, they will highly likely to be no more prone to erroneousness than any other human invention.
 If evolutionary and development psychology is taken into account, the first members of fully autonomous social robots will also evolve rapidly to their excellence.
+%prepare individuals, societies and governments its coming
 As the expansion and the accessibility to AI and robotics increase, the prediction of the aftermath has become decrepit due to the late response of individuals and their wisdom toward these technologies.

### 2015-06-13 draft1.tex
Last commit after Cenk was admitted

@@
 % Since robots can be regarded self-conscience agents, thanks to advanced reasoning, cognitive and perceptual abilities provided by AI, 
-Akin to the nature of any given invention, the ultimate reason for the invention of robots is the elevation of life conditions and inquiry for applicable solutions for problems of societies.
+Akin to the nature of any given invention, the ultimate reason for the invention of robots is the elevation of life conditions and inquiry about applicable solutions for societal problems.
 However, a major issue having been discussed is whether or not military, one of the biggest supporter of robotics, is being sincere with its funding purposes \cite{gre}.
@@
 By literary definition the term robot is derived from the Czech word "roboti" meaning serf-labor. 
-However, this definition closely referring to slave-like labourer has been altered to something brand new as technology advances.
+However, this definition closely referring to slave-like laborer has become something brand new as technology advances.
 In his article entitled "The Sheer Difficulty of Defining What a Robot Is", \citeA{pear} discusses two distinctive definitions of robotics that are posed by the prominent experts in the field of robotics.
@@
 Without a software and hardware collaboration, as \citeA{pear} cites in his article, accomplishing its tasks for a robot cannot be possible.
-
 The second definition, however, takes autonomy into account.
 A robot, \citeA{pear} quotes in his article, must have an detailed idea of any action formed by a tedious plan, accurate reasoning and precise action to interact with its physical environment which closely aligns with the definition provided by \cite{lin}.
-\citeauthor{lin} \citeyear[p.~943]{lin} define a robots as "an engineered machine that senses, thinks, and acts".
-In light of these definitions, robots have to interact with its environment, which exclude any means of social interactions.
+\citeauthor{lin} \citeyear[p.~943]{lin} define a robot as "an engineered machine that senses, thinks, and acts".
+In light of these definitions, robots have to interact with its environment. However, such definitions exclude any means of social interactions.
 However, \citeA{lan} asserts that socially interaction robots are significantly popular in society.
-
 %Albeit popular, social robots, for instance a teacher robot or a guidance robot employed in an art gallery, seem to be decontextualized.
-
-This discrepancy brings about a major problem at the individual and societal levels.
+This discrepancy brings about a major problem on the individual and societal levels.
 One example of this fact is that individuals have started to get strong advice from AI applications, a software crunching numbers faster than a man can do, rather than a close friend who might know better about the individual seeking advice, such as the taste in music or book.
@@
 In order to make its obfuscated definition clear, the tasks of AI should be addressed.
-On the one hand,  \citeA[p.~943]{lin} note that robots are supposedly employed in such tasks called "three D's" referring "dull, dirty, or dangerous" tasks.
+On the one hand,  \citeA[p.~943]{lin} note that robots are employed in such tasks called "three D's" referring "dull, dirty, or dangerous" tasks.
 From that instruction, a robot should replace human where the task contains either mundane chores, or risks of contamination, or threatening factors for human lives.
@@
 %Along with the definitions of robotics, the applications of it extensively vary which makes it hard to define or understand the task and the responsibilities of robots.
-On the other hand, \citeA{lan} and \citeA{lin} list many different real life robotic applications, from labourer robots to medical purpose robots and to personal care and companion robots, which contradicts with given instruction.
+On the other hand, \citeA{lan} and \citeA{lin} list many different real life robotic applications, from laborer robots to medical purpose robots and to personal care and companion robots, which contradicts with given instruction.
 While \citeA{pear} also excludes any means of social interaction in the definitions of robotics proposed in this article, \citeA{rodhan} elaborates this issue by indicating an emerging application of robotics, a molecular level robot which identifies cancerous cells and attack them by releasing antibodies, thereby eliminating cancerous cells.

### 2015-06-15 draft1.tex
Implement changes that Professor Correa suggested

@@
 % modify it!
-\abstract{Of all the tools and methods invented by humankind to tame nature and make use of its challenges, the invention of computer has had the greatest impact on society.
-Coupled with the Internet, computers have changed the way billions of humans work, entertain themselves, and think.
-Since the rise of the computers, Artificial Intelligence (AI) has been one of the most debated issues in the field of engineering.
-Robots are also subject to these debates because that tangible spin-off technology that will be run by such an AI that will have superior cognitive and perceptive abilities than that of man. 
+\abstract{Artificial Intelligence (AI) has been one of the most debated issues in the field of engineering.
+Robots are also subject to these debates because that tangible spin-off technology that will be run by such an AI that will have superior cognitive and perceptive abilities than that of humankind. 
 Many researchers argue that the creation of AI will deeply elevate society and it will help humankind to solve major societal problems, while others refute the arguments for that conceptual invention.
@@
 Sometimes, solutions for any arbitrary problem can be addressed by seeing the bigger picture rather than scrutinizing tiny details.
-Thus, this paper explores these problems and then analyzes the numerous definitions and applications of these technologies which pose challenges on varying levels, from individual to societal.
-The formation of this paper is as follows: The first section categorizes the issues that robotics have arisen; the second and third sections then scrutinize the definitions and the applications of robots, respectively, to attribute the reasons of these issues.
-
-\section{The Most Profound Issues of Robotics}
-From the very early contemplations of AI, it has been the most controversial issue within the engineering and scientific societies due to its ethical problems.
-Near future is fecund to many dilemmas which humankind, soon or later, will face regarding AI's moral integrity and its position in society.
-This section synthesizes the issues of employment of AI and robots in a wide spectrum of tasks.
-
-\subsection{Safety Issues}
-% Since robots can be regarded self-conscience agents, thanks to advanced reasoning, cognitive and perceptual abilities provided by AI, 
-Akin to the nature of any given invention, the ultimate reason for the invention of robots is the elevation of life conditions and inquiry about applicable solutions for societal problems.
-However, a major issue having been discussed is whether or not military, one of the biggest supporter of robotics, is being sincere with its funding purposes \cite{gre}.
-Of the many supporters of such research studies, military appears to be the most questionable one due to plausible intentions of creation of humanoid army.
-% <readagain>
-This utilization of a weaponized robotic army would boost the vast possession of ammunition problem instead of mediating inter-governmental conflicts.
-% </readagain>
-This contentious utilization of battlefield robots is one of the biggest concern when it comes to mediate inter-governmental conflicts.
-Such probability may put countries in circumstances resembling strongly to the Cold War.
-\par
-
-% Add Hacking Section
-
-% Add human proneness to fail and errors in source code. (skepticism and uncanny)
-
-\subsection{Legal and Ethical Issues}
-Robots are envisioned to be controlled by a such intelligence which enable their to perceive their surrounding environments where they interact with the objects by themselves.
-Thus, they can be regarded as independent agents.
-This conceptual freedom, however, raises an ethical dilemma caused by the absence of legal ramifications of AI.
-\citeA{gre} examine that ambiguity by posing a controversial question: "Who will be responsible for results of AI's actions and failure?"
-Since the contemplation of AI and robots indicates that robots will supposedly make their own choices take actions according to these choices, another interesting question arises: "Would robots be prosecuted -maybe executed- because of the fails they commit?"
-Similar to the questions above, there are many questions that governments need to address by creating regulations and laws under which robots will be positioned. \par
-Furthermore, many researchers has been questioning whether or not these super-intelligent agents should have duties to society; if so, to what extent governments should give social rights to robots.
-\citeA{bob} addresses this issue by underlining basic rights and duties of citizens such as taxing and voting.
-In other words, not only does AI's legal ramification matter, but it is also equally important for governments to decide the AI's responsibility for the society, vice versa.
-To address this issue, \citeA{kerb} analyzes Japanese artworks showing futuristic plots based upon robots cohabitating and interacting with humans.
-These artworks depicts the very early speculations of social equality between man and machine regarding civil and political rights among.
-Kerb's evaluation of these artworks concludes that robots, depicted and envisioned in the artworks, are neither overlords nor serf-laborers.
-
-\subsection{Psychological Challenges and Socio-economic Issues}
-Social interaction is what differentiates humans from machines.
-However, as the research studies toward creation of AI have gone deeper, robots have become more socially interactive within society.
-For instance, before GPS became publicly available, route planning was based upon map-reading and asking directions of the locals.
-In light of this example, AI has become route planning assistant and has decreased the interrelation among individuals.
-According to \citeA{lan}, reformation of our perception towards AI poses misconceptions regarding personhood and promotes loneliness.
-This issue truly matters due to the fact that alienation from the society relies on that misconception.
-Another matter that deeply affects human psychology is that innovative superiority of robots seems to increase profitability and efficiency, albeit undermining the true value of failures.
-Given that failures are one of most essential component of human learning process, superiority of AI discourage individuals to commit any form of actions due to fear of failures. 
-This fear impedes the same body of individuals to learn and trust human judgment, hindering them completely.
-Depression and other similar psychological challenges are the most profound indicators of the aftermaths of inaccurate definition of AI. \par
-
-Furthermore, the rise of computers has led to lessen the human employment starting from late 70's.
-Because of the downsizing tendency of corporations which resulted from this replacement, millions of low-skilled workers lost their jobs.
-Robots and AI supposedly represent the maxima of accuracy and repeatability which promotes reliance on AI thanks to their cognitive and learning abilities that outperform human abilities.
-Given that historic fact, \citeA{gre} predict that this reliance might cause an inevitable replacement of low-skilled laborers with the more powerful robots, akin to aftermaths of the computerization era.
-In light of that prediction, highly developed economies may show a strong recession due to the significant lost in human work power and if this aggressive expansion continues, other occupations and professions will be under the same risk of mechanization.
-\par
-
-Along with the economical effects of workplace computerization, eradication of low-skilled jobs may lead the expansion of the gap among the social groups \cite{gre}.
-For instance, as the first paragraph of this section indicates, those who can use computers or know developing software have reached to higher classes in societies, while other could not seize the same momentum.
-This computerization instruct young individual belong to lower layers of society to believe that there is no way to elevate in society.
-This expansion in the gap with in society and among the social groups clearly contradicts to the societal goals of robotics.
+Thus, this paper explores problems related to legal, ethical frameworks and then analyzes the numerous definitions and applications of these technologies which pose challenges on varying levels, from individual to societal.
+The formation of this paper is as follows: The second and third sections then scrutinize the definitions and the applications of robots, respectively, to attribute the reasons for these issues, and the third section categorizes the issues that robotics have arisen.
 
@@
 The second definition, however, takes autonomy into account.
-A robot, \citeA{pear} quotes in his article, must have an detailed idea of any action formed by a tedious plan, accurate reasoning and precise action to interact with its physical environment which closely aligns with the definition provided by \cite{lin}.
+A robot, \citeA{pear} quotes in his article, must have an detailed idea of any action formed by a tedious plan, accurate reasoning and precise action to interact with its physical environment, which closely aligns with the definition provided by \cite{lin}.
 \citeauthor{lin} \citeyear[p.~943]{lin} define a robot as "an engineered machine that senses, thinks, and acts".
-In light of these definitions, robots have to interact with its environment. However, such definitions exclude any means of social interactions.
-However, \citeA{lan} asserts that socially interaction robots are significantly popular in society.
+In light of these definitions, robots have to interact with its environment.
+However, such definitions exclude any means of social interactions, even though \citeA{lan} asserts that socially interactive robots are significantly popular in society.
 %Albeit popular, social robots, for instance a teacher robot or a guidance robot employed in an art gallery, seem to be decontextualized.
@@
 \par
+\section{The Most Profound Issues of Robotics}
+From its very early contemplations of AI, it has been the most controversial issue within the engineering and scientific societies due to its ethical problems.
+Near future is fecund to many dilemmas which humankind, soon or later, will face regarding AI's moral integrity and its position in society.
+This section synthesizes the issues of employment of AI and robots in a wide spectrum of tasks.
+
+\subsection{Safety Issues}
+% Since robots can be regarded self-conscience agents, thanks to advanced reasoning, cognitive and perceptual abilities provided by AI, 
+Akin to the nature of any given invention, the ultimate reason for the invention of robots is the elevation of life conditions and inquiry about applicable solutions for societal problems.
+However, a major issue having been discussed is whether or not the military, one of the biggest supporter of robotics, is being sincere with its funding purposes \cite{gre}.
+Of the many supporters of such research studies, the military appears to be the most questionable one due to plausible intentions of creation of humanoid army.
+% <readagain>
+This utilization of a weaponized robotic army would boost the vast possession of ammunition problem instead of mediating inter-governmental conflicts.
+% </readagain>
+This contentious utilization of battlefield robots is one of the biggest concerns when it comes to mediate inter-governmental conflicts.
+Such probability may put countries in circumstances resembling strongly to the Cold War.
+\par
+
+% Add Hacking Section
+
+% Add human proneness to fail and errors in source code. (skepticism and uncanny)
+
+\subsection{Legal and Ethical Issues}
+Furthering concerns about their military applications, robots are envisioned to be controlled by a such intelligence which enable their to perceive their surrounding environments where they interact with the objects by themselves.
+Thus, robots can be regarded as independent agents.
+This conceptual freedom, however, raises an ethical dilemma caused by the absence of legal ramifications of AI.
+\citeA{gre} examine that ambiguity by posing a controversial question: "Who will be responsible for results of AI's actions and failure?"
+Since the contemplation of AI and robots indicates that robots will supposedly make their own choices to take actions according to these choices, another interesting question arises: "Would robots be prosecuted -maybe executed- because of the fails they commit?"
+Similar to the questions above, there are many questions that governments need to address by creating regulations and laws under which robots will be positioned. \par
+Furthermore, many researchers have been questioning whether or not these super-intelligent agents should have duties, such as taxing, to society; if so, to what extent governments should give social rights to robots.
+\citeA{bob} addresses this issue by underlining basic rights and duties of citizens such as taxing and voting.
+In other words, not only does AI's legal ramification matter, but it is also equally important for governments to decide the AI's responsibility for the society, vice versa.
+To address this issue, \citeA{kerb} analyzes Japanese artworks showing futuristic plots based upon robots cohabitating and interacting with humans.
+These artworks depicts the very early speculations of social equality between man and machine regarding civil and political rights among.
+Kerb's evaluation of these artworks concludes that robots, depicted and envisioned in the artworks, are neither overlords nor serf-laborers.
+
+\subsection{Psychological Challenges and Socio-economic Issues}
+Social interaction is what differentiates humans from machines.
+However, as the research studies toward creation of AI have gone deeper, robots have become more socially interactive within society.
+For instance, before GPS became publicly available, route planning was based upon map-reading and asking directions of the locals.
+In light of this example, AI has become route planning assistant and has decreased the interrelation among individuals.
+According to \citeA{lan}, reformation of our perception towards AI poses misconceptions regarding personhood and promotes loneliness.
+This issue truly matters due to the fact that alienation from the society relies on that misconception.
+Another matter that deeply affects human psychology is that innovative superiority of robots seems to increase profitability and efficiency in workplaces, albeit undermining the true value of failures.
+Given that failures are one of most essential component of human learning process, superiority of AI tend to discourage individuals to commit any form of actions due to fear of failures. 
+This fear impedes the same body of individuals to learn, hindering them completely to trust human judgment .
+Depression and other similar psychological challenges are the most profound indicators of the aftermaths of inaccurate definition of AI. \par
+
+Furthermore, the rise of computers has led to lessen the human employment starting from late 70's.
+Because of the downsizing tendency of corporations which resulted from this replacement, millions of low-skilled workers lost their jobs.
+Robots and AI supposedly represent the maxima of accuracy and repeatability, which promotes reliance on AI thanks to their cognitive and learning abilities that outperform human abilities.
+Given that historic fact, \citeA{gre} predict that this reliance might cause an inevitable replacement of low-skilled laborers with the more powerful robots, akin to the aftermaths of the computerization era.
+In light of that prediction, highly developed economies may show a strong recession due to the significant loss in human work power and if this aggressive expansion continues, other occupations and professions will be under the same risk of mechanization.
+\par
+
+Along with the economical effects of workplace computerization, eradication of low-skilled jobs may lead to the expansion of the gap among the social groups \cite{gre}.
+For instance, as the first paragraph of this section indicates, those who can use computers or know how to develop software have reached to higher classes in societies, while others could not seize the same momentum.
+This computerization instructs young individual belong to lower layers of society to believe that there is no way to elevate in society.
+This expansion in the gap with in society and among the social groups clearly contradicts to the societal goals of robotics.
 
 \section{Conclusion}
-The notion of increasingly accelerating technology with the precious help of scientific research studies thrills individuals, and gives hope to patients.
+The notion of increasingly accelerating technology with the precious help of scientific research studies thrills individuals.
 %However, these two prominent concepts of technology closely resembles another, the Internet.
@@
 In that case, the matter should be discussed would be how to mitigate, even eradicate, human errors taking place when roboticists develop robots and AI. \par
-As for the ethical problems, they will highly likely to be no more prone to erroneousness than any other human invention.
+As for the ethical problems, robots will highly likely to be no more prone to erroneousness than any other human invention.
 If evolutionary and development psychology is taken into account, the first members of fully autonomous social robots will also evolve rapidly to their excellence.
 %prepare individuals, societies and governments its coming
-As the expansion and the accessibility to AI and robotics increase, the prediction of the aftermath has become decrepit due to the late response of individuals and their wisdom toward these technologies.
+As the expansion and the accessibility to AI and robotics increase, the prediction of the aftermath has become obsolete due to the late response of individuals and their wisdom toward these technologies.
 Thus, robotics and AI should be scrutinized to understand and formulate its definitions and functions, otherwise yet another issue will jump into debate topics before formers could be solved.

### 2015-06-15 draft1.tex
Comment out GPS Example and Move the misconceptions regarding AI becoming a person to the evaluation

@@
 
-\section{The Bigger Picture}
-\subsection{What is a Robot?}
+\section{What is a Robot?}
 %One common definition of AI is cited by \citeA{bost}, "A super-intelligence is any intellect that vastly outperforms the best human brains in practically every field, including scientific creativity, general %wisdom and social skills."
@@
 \citeauthor{lin} \citeyear[p.~943]{lin} define a robot as "an engineered machine that senses, thinks, and acts".
-In light of these definitions, robots have to interact with its environment.
-However, such definitions exclude any means of social interactions, even though \citeA{lan} asserts that socially interactive robots are significantly popular in society.
-%Albeit popular, social robots, for instance a teacher robot or a guidance robot employed in an art gallery, seem to be decontextualized.
-This discrepancy brings about a major problem on the individual and societal levels.
-One example of this fact is that individuals have started to get strong advice from AI applications, a software crunching numbers faster than a man can do, rather than a close friend who might know better about the individual seeking advice, such as the taste in music or book.
-Even though this issue seems to have a minor flipside, once it is aggregated \citeA{lan} claims, it will create true alienation from society and confusion regarding personhood.
 In other words, roboticists have not been able  to reach a consensus on the definition of robots the embodiment of AI, \citeA{lin} note.
@@
 
-\subsection{What (should) does a Robot do?}
+\section{What (should) does a Robot do?}
 % A strip from the old paper
@@
 However, as the research studies toward creation of AI have gone deeper, robots have become more socially interactive within society.
-For instance, before GPS became publicly available, route planning was based upon map-reading and asking directions of the locals.
-In light of this example, AI has become route planning assistant and has decreased the interrelation among individuals.
-According to \citeA{lan}, reformation of our perception towards AI poses misconceptions regarding personhood and promotes loneliness.
-This issue truly matters due to the fact that alienation from the society relies on that misconception.
+%For instance, before GPS became publicly available, route planning was based upon map-reading and asking directions of the locals.
+%In light of this example, AI has become route planning assistant and has decreased the interrelation among individuals.
+%According to \citeA{lan}, reformation of our perception towards AI poses misconceptions regarding personhood and promotes loneliness.
+%This issue truly matters due to the fact that alienation from the society relies on that misconception.
+In light of definitions given in the first section, robots have to interact with their physical environment.
+However, such definitions exclude any means of social interactions, even though \citeA{lan} asserts that socially interactive robots are significantly popular in society.
+%Albeit popular, social robots, for instance a teacher robot or a guidance robot employed in an art gallery, seem to be decontextualized.
+This discrepancy brings about a major problem on the individual and societal levels.
+One example of this fact is that individuals have started to get strong advice from AI applications, a software crunching numbers faster than a man can do, rather than a close friend who might know better about the individual seeking advice, such as the taste in music or book.
+Even though this issue seems to have a minor flipside, once it is aggregated \citeA{lan} claims, it will create true alienation from society and confusion regarding personhood. \par
 Another matter that deeply affects human psychology is that innovative superiority of robots seems to increase profitability and efficiency in workplaces, albeit undermining the true value of failures.

### 2015-06-15 draft1.tex
Implement fixes to errors that Ruth realized

@@
 Thus, this paper explores problems related to legal, ethical frameworks and then analyzes the numerous definitions and applications of these technologies which pose challenges on varying levels, from individual to societal.
-The formation of this paper is as follows: The second and third sections then scrutinize the definitions and the applications of robots, respectively, to attribute the reasons for these issues, and the third section categorizes the issues that robotics have arisen.
+The formation of this paper is as follows: The first and second sections scrutinize the definitions and the applications of robots, respectively, to attribute the reasons for these issues, and the third section then categorizes the issues that robotics have brought about.
 
@@
 
-By literary definition the term robot is derived from the Czech word "roboti" meaning serf-labor. 
-However, this definition closely referring to slave-like laborer has become something brand new as technology advances.
+By literary definition the term robot is derived from the Czech word "roboti" meaning serf-laborer. 
+However, this definition closely referring to a slave-like laborer has become something brand new as technology advances.
 In his article entitled "The Sheer Difficulty of Defining What a Robot Is", \citeA{pear} discusses two distinctive definitions of robotics that are posed by the prominent experts in the field of robotics.
 These two definitions emphasize different aspects of robotics creating important distinctions among them.
-The first definition puts emphasis on the successful combination of a rigid body responsible for interacting with its environment and a central reasoning unit responsible for reasoning tasks based perception and cognition.
-Without a software and hardware collaboration, as \citeA{pear} cites in his article, accomplishing its tasks for a robot cannot be possible.
+The first definition puts emphasis on the successful combination of a rigid body responsible for interacting with its environment and a central processing unit responsible for reasoning tasks based on perception and cognition.
+A robot cannot accomplish its tasks without a software and hardware collaboration, as \citeA{pear} cites in his article.
 The second definition, however, takes autonomy into account.
-A robot, \citeA{pear} quotes in his article, must have an detailed idea of any action formed by a tedious plan, accurate reasoning and precise action to interact with its physical environment, which closely aligns with the definition provided by \cite{lin}.
+A robot, \citeA{pear} quotes in his article, must have a detailed idea of any action formed by a rigorous plan, accurate reasoning and precise action to interact with its physical environment, which closely aligns with the definition provided by \cite{lin}.
 \citeauthor{lin} \citeyear[p.~943]{lin} define a robot as "an engineered machine that senses, thinks, and acts".
-In other words, roboticists have not been able  to reach a consensus on the definition of robots the embodiment of AI, \citeA{lin} note.
+In other words, roboticists have not been able  to reach a consensus on the definition of robots, the embodiment of AI, \citeA{lin} note.
 \par
 
-\section{What (should) does a Robot do?}
+\section{What (should / does) a Robot do?}
 % A strip from the old paper
 In order to make its obfuscated definition clear, the tasks of AI should be addressed.
-On the one hand,  \citeA[p.~943]{lin} note that robots are employed in such tasks called "three D's" referring "dull, dirty, or dangerous" tasks.
-From that instruction, a robot should replace human where the task contains either mundane chores, or risks of contamination, or threatening factors for human lives.
+On the one hand,  \citeA[p.~943]{lin} note that robots are employed in tasks called "three D's" referring to "dull, dirty, or dangerous" tasks.
+From that instruction, a robot should replace a human where the task contains either mundane chores, or risks of contamination, or threats to human lives.
 \par 
@@
 %Along with the definitions of robotics, the applications of it extensively vary which makes it hard to define or understand the task and the responsibilities of robots.
-On the other hand, \citeA{lan} and \citeA{lin} list many different real life robotic applications, from laborer robots to medical purpose robots and to personal care and companion robots, which contradicts with given instruction.
-While \citeA{pear} also excludes any means of social interaction in the definitions of robotics proposed in this article, \citeA{rodhan} elaborates this issue by indicating an emerging application of robotics, a molecular level robot which identifies cancerous cells and attack them by releasing antibodies, thereby eliminating cancerous cells.
-Even though experts have not been able to solve dilemmas within the field of robotics, this continuum of sophistication within robotics add more complex issues to the pile.
+On the other hand, \citeA{lan} and \citeA{lin} list many different real-life robotic applications, from laborer robots to medical-purpose robots and to personal care and companion robots, which contradicts the "Three D's".
+While \citeA{pear} also excludes any means of social interaction in the definitions of robotics proposed in this article, \citeA{rodhan} elaborates on this issue by indicating an emerging application of robotics, a molecular level robot which identifies cancerous cells and attacks them by releasing antibodies, thereby eliminating cancerous cells.
+Even though experts have not been able to solve dilemmas within the field of robotics, this continuum of sophistication within robotics adds more complex issues to the pile.
 % The reason why these social interaction dilemma matter, whether in bodily level or molecular level, is that technology advances in faster pace than that of the wisdom regarding robots and ourselves.
@@
 \section{The Most Profound Issues of Robotics}
-From its very early contemplations of AI, it has been the most controversial issue within the engineering and scientific societies due to its ethical problems.
-Near future is fecund to many dilemmas which humankind, soon or later, will face regarding AI's moral integrity and its position in society.
+From its very early contemplations, AI has been the most controversial issue within the engineering and scientific societies due to its ethical problems.
+The near future is fecund with many dilemmas which humankind, sooner or later, will face regarding AI's moral integrity and its position in society.
 This section synthesizes the issues of employment of AI and robots in a wide spectrum of tasks.
@@
 Akin to the nature of any given invention, the ultimate reason for the invention of robots is the elevation of life conditions and inquiry about applicable solutions for societal problems.
-However, a major issue having been discussed is whether or not the military, one of the biggest supporter of robotics, is being sincere with its funding purposes \cite{gre}.
-Of the many supporters of such research studies, the military appears to be the most questionable one due to plausible intentions of creation of humanoid army.
+However, a major issue being discussed is whether or not the military, one of the biggest supporters of robotics, is being sincere with its funding purposes \cite{gre}.
+Of the many supporters of such research studies, the military appears to be the most questionable one due to plausible intentions of creation of a humanoid army.
 % <readagain>
-This utilization of a weaponized robotic army would boost the vast possession of ammunition problem instead of mediating inter-governmental conflicts.
+This utilization of a weaponized robotic army would boost the vast possession of ammunition instead of mediating inter-governmental conflicts.
 % </readagain>
-This contentious utilization of battlefield robots is one of the biggest concerns when it comes to mediate inter-governmental conflicts.
-Such probability may put countries in circumstances resembling strongly to the Cold War.
-\par
+This contentious utilization of battlefield robots is one of the biggest concerns when it comes to resolving inter-governmental conflicts.
+Such probability may put countries in circumstances strongly resembling to the Cold War. \par
 
@@
 \subsection{Legal and Ethical Issues}
-Furthering concerns about their military applications, robots are envisioned to be controlled by a such intelligence which enable their to perceive their surrounding environments where they interact with the objects by themselves.
+Furthering concerns about their military applications, robots are envisioned to be controlled by an intelligence which will enable them to perceive their surrounding environments where they can interact with objects by themselves.
 Thus, robots can be regarded as independent agents.
-This conceptual freedom, however, raises an ethical dilemma caused by the absence of legal ramifications of AI.
+This conceptual freedom, however, raises an ethical dilemma caused by the absence of legal ramifications for AI.
 \citeA{gre} examine that ambiguity by posing a controversial question: "Who will be responsible for results of AI's actions and failure?"
-Since the contemplation of AI and robots indicates that robots will supposedly make their own choices to take actions according to these choices, another interesting question arises: "Would robots be prosecuted -maybe executed- because of the fails they commit?"
+Since the contemplation of AI and robots indicates that robots will supposedly make their own choices to take actions according to these choices, another interesting question arises: "Would robots be prosecuted -maybe executed- because of their failures?"
+The first human killed by a robot is believed to take place in late 70's, in an industrial complex \cite{lin}.
 Similar to the questions above, there are many questions that governments need to address by creating regulations and laws under which robots will be positioned. \par

### 2015-06-15 draft1.tex
Edit the Conclusions section

@@
 This conceptual freedom, however, raises an ethical dilemma caused by the absence of legal ramifications for AI.
-\citeA{gre} examine that ambiguity by posing a controversial question: "Who will be responsible for results of AI's actions and failure?"
+The first fatal accident resulted killing a laborer by a robot is believed to took place in late 70's, in an industrial complex \cite{lin}.
+\citeA{gre} examine that ambiguity by posing a controversial question: "Who will be responsible for results of AI's actions and failures?"
 Since the contemplation of AI and robots indicates that robots will supposedly make their own choices to take actions according to these choices, another interesting question arises: "Would robots be prosecuted -maybe executed- because of their failures?"
-The first human killed by a robot is believed to take place in late 70's, in an industrial complex \cite{lin}.
 Similar to the questions above, there are many questions that governments need to address by creating regulations and laws under which robots will be positioned. \par
-Furthermore, many researchers have been questioning whether or not these super-intelligent agents should have duties, such as taxing, to society; if so, to what extent governments should give social rights to robots.
+Furthermore, many researchers have been questioning whether or not these super-intelligent agents should have duties to society, such as taxing; if so, to what extent governments should give social rights to robots.
 \citeA{bob} addresses this issue by underlining basic rights and duties of citizens such as taxing and voting.
@@
 These artworks depicts the very early speculations of social equality between man and machine regarding civil and political rights among.
-Kerb's evaluation of these artworks concludes that robots, depicted and envisioned in the artworks, are neither overlords nor serf-laborers.
 
@@
 However, such definitions exclude any means of social interactions, even though \citeA{lan} asserts that socially interactive robots are significantly popular in society.
-%Albeit popular, social robots, for instance a teacher robot or a guidance robot employed in an art gallery, seem to be decontextualized.
+Albeit popular, social robots, for instance a teacher robot or a guidance robot employed in an art gallery, appears to be decontextualized with regards to definitions provided in the first section.
 This discrepancy brings about a major problem on the individual and societal levels.
 One example of this fact is that individuals have started to get strong advice from AI applications, a software crunching numbers faster than a man can do, rather than a close friend who might know better about the individual seeking advice, such as the taste in music or book.
-Even though this issue seems to have a minor flipside, once it is aggregated \citeA{lan} claims, it will create true alienation from society and confusion regarding personhood. \par
-Another matter that deeply affects human psychology is that innovative superiority of robots seems to increase profitability and efficiency in workplaces, albeit undermining the true value of failures.
+Even though this issue seems to have a minor flip-side, once it is aggregated \citeA{lan} claims, it will create true alienation from society and confusion regarding personhood. \par
+Another matter that deeply affects human psychology is that innovative superiority of robots seems to increase profitability and efficiency in workplaces, thereby undermining the true value of failures.
 Given that failures are one of most essential component of human learning process, superiority of AI tend to discourage individuals to commit any form of actions due to fear of failures. 
@@
 
-\section{Conclusion}
+\section{Conclusions}
 The notion of increasingly accelerating technology with the precious help of scientific research studies thrills individuals.
@@
 Yet, it is crucially important to decide whether or not robots are simply functional machines that are utilitarian in their responsibilities and nothing more.
-If so, it is irrelevant to discuss the ethical problems arisen by its creation because the problems will become a question of accuracy of the source code that runs robots and forms AI.
+If so, it is irrelevant to discuss the ethical problems arisen by its creation because the problems will become a question of accuracy of the source code that runs robots and.
 In that case, the matter should be discussed would be how to mitigate, even eradicate, human errors taking place when roboticists develop robots and AI. \par
-As for the ethical problems, robots will highly likely to be no more prone to erroneousness than any other human invention.
-If evolutionary and development psychology is taken into account, the first members of fully autonomous social robots will also evolve rapidly to their excellence.
-%prepare individuals, societies and governments its coming
-As the expansion and the accessibility to AI and robotics increase, the prediction of the aftermath has become obsolete due to the late response of individuals and their wisdom toward these technologies.
-Thus, robotics and AI should be scrutinized to understand and formulate its definitions and functions, otherwise yet another issue will jump into debate topics before formers could be solved.
+As for the ethical problems, there are two distinctive approaches to the future of robots.
+The first one is that robots will highly likely to be no more prone to erroneousness than any other human invention.
+If evolutionary psychology is taken into account, the first members of fully autonomous robots will also evolve rapidly toward their excellence.
+Moreover, the second approach claims that as the expansion and the accessibility to AI and robotics increase, the prediction of the aftermath has become obsolete due to the late response of individuals and their wisdom toward these technologies.
+Thus, robotics should be scrutinized by various roboticists, scientists, ethicists, psychologists, sociologists and many other experts to understand and formulate its limitations and endless possibilities, otherwise yet another issue will accumulate into debate topics before former ones could be solved.
+
+%\cite{Kerb}'s evaluation of the Japanese artworks concludes that robots, depicted and envisioned in the artworks, are neither overlords nor serf-laborers. 
 \bibliographystyle{apacite}

### 2015-06-15 draft1.tex
Add Hacking and Human Error to Safety Issues

@@
 
-% Add Hacking Section
+% Add human proneness to fail and errors in source code. (skepticism and uncanny)
+Coupled with the military concerns, human errors in source code is yet another issue impeding roboticists to develop the software.
+As computers scientists, fallible human beings, compile millions of lines of code into one perfect software, the risk of emergence of code that makes a robot to prone to fail in any given task is soaring.
+A tiny flaw on software level, \citeA{lin} note, can lead to fatal results.
 
-% Add human proneness to fail and errors in source code. (skepticism and uncanny)
+Moreover, hacking has been the most debated issue since the Internet became publicly available.
+Along with many other safety issues, hacking is an associated one regarding how to securely integrate robots in work settings.
+In this case, the risk is not identity theft or any other illegal activities since the anticipations for robots to be employed in wide variety of tasks.
+If a hacker can grant access in an uncanny way to robots' central processing unit, s/he can make the robot commit any action s/he wants.
+So, all the superior abilities \citeA[p.~4]{lin}, namely, "its strength, ability to access and operate in difficult environments, expendability and so on", may be turned against society.
+This possibility clearly contradicts the ultimate goal of creation of robots.
 
@@
 Since the contemplation of AI and robots indicates that robots will supposedly make their own choices to take actions according to these choices, another interesting question arises: "Would robots be prosecuted -maybe executed- because of their failures?"
-Similar to the questions above, there are many questions that governments need to address by creating regulations and laws under which robots will be positioned. \par
+Similar to the questions above, there are many questions that governments need to address by creating regulations and laws with which robots will comply. \par
 Furthermore, many researchers have been questioning whether or not these super-intelligent agents should have duties to society, such as taxing; if so, to what extent governments should give social rights to robots.
@@
 In light of definitions given in the first section, robots have to interact with their physical environment.
-However, such definitions exclude any means of social interactions, even though \citeA{lan} asserts that socially interactive robots are significantly popular in society.
+However, such definitions exclude any means of human interactions, even though \citeA{lan} asserts that socially interactive robots are significantly popular in society.
 Albeit popular, social robots, for instance a teacher robot or a guidance robot employed in an art gallery, appears to be decontextualized with regards to definitions provided in the first section.

### 2015-06-16 manuscript.tex
Edit for the last commit for 6/15/2015

--- 2015-06-15 draft1.tex
@@
 This contentious utilization of battlefield robots is one of the biggest concerns when it comes to resolving inter-governmental conflicts.
-Such probability may put countries in circumstances strongly resembling to the Cold War. \par
-
-% Add Hacking Section
+Such probability may put countries in circumstances strongly resembling the Cold War. \par
 
 % Add human proneness to fail and errors in source code. (skepticism and uncanny)
+Coupled with the military concerns, human source code errors are yet another issue impeding roboticists from developing the software.
+As computer scientists, fallible human beings, compile millions of lines of code into one "perfect" software, the risk of robot failure due to errors in the code is soaring.
+A tiny flaw on the software level, \citeA{lin} note, can lead to fatal results.
+
+Moreover, hacking has been the most debated issue since the Internet became publicly available.
+Along with many other safety issues, hacking is an associated issue regarding when it comes to securely integrating robots in work settings.
+In this case, the risk is not identity theft or any other illegal activity. % since the anticipations for robots to be employed in wide variety of tasks.
+If a hacker can grant access in a cryptic way to the robots' central processing unit, s/he can make the robot commit any action s/he wants.
+So, all of the superior abilities, namely, "its strength, ability to access and operate in difficult environments, expendability and so on", may be turned against society \cite[p.~945]{lin}.
+This possibility clearly contradicts the ultimate goal of the creation of robots.
 
@@
 This conceptual freedom, however, raises an ethical dilemma caused by the absence of legal ramifications for AI.
-The first fatal accident resulted killing a laborer by a robot is believed to took place in late 70's, in an industrial complex \cite{lin}.
-\citeA{gre} examine that ambiguity by posing a controversial question: "Who will be responsible for results of AI's actions and failures?"
-Since the contemplation of AI and robots indicates that robots will supposedly make their own choices to take actions according to these choices, another interesting question arises: "Would robots be prosecuted -maybe executed- because of their failures?"
-Similar to the questions above, there are many questions that governments need to address by creating regulations and laws under which robots will be positioned. \par
-Furthermore, many researchers have been questioning whether or not these super-intelligent agents should have duties to society, such as taxing; if so, to what extent governments should give social rights to robots.
-\citeA{bob} addresses this issue by underlining basic rights and duties of citizens such as taxing and voting.
-In other words, not only does AI's legal ramification matter, but it is also equally important for governments to decide the AI's responsibility for the society, vice versa.
-To address this issue, \citeA{kerb} analyzes Japanese artworks showing futuristic plots based upon robots cohabitating and interacting with humans.
-These artworks depicts the very early speculations of social equality between man and machine regarding civil and political rights among.
+The first fatal accident that resulted in a killing of a laborer by a robot is believed to have taken place in the late 70's \cite{lin}.
+\citeA{gre} examine that ambiguity by posing a controversial question: "Who will be responsible for the results of AI's actions and failures?"
+Since the contemplation of AI and robots replacing laborers in some tasks indicates that robots will supposedly make their own choices to take actions according to these choices, another interesting question arises: "Would robots be prosecuted -maybe executed- because of their failures?"
+Similar to the questions above, there are many questions that governments need to address by creating regulations and laws with which robots will comply. \par
+Furthermore, many researchers have been questioning whether or not these super-intelligent agents should have duties to society, such as paying taxes; if so, to what extent should governments  give social rights to robots?
+\citeA{bob} addresses this issue by underlining basic rights and duties of citizens such as paying taxes and voting.
+In other words, not only does AI's legal ramification matter, but it is also equally important for governments to decide the AI's responsibility to society, and vice versa.
+To address this issue, \citeA{kerb} analyzes Japanese artwork showing futuristic plots based upon robots cohabitating and interacting with humans.
+This artwork depicts the very early speculations of social equality between man and machine regarding civil and political rights.
 
@@
 Social interaction is what differentiates humans from machines.
-However, as the research studies toward creation of AI have gone deeper, robots have become more socially interactive within society.
+However, as the research studies toward creation of AI have gone deeper, robots have become more socially interactive with society.
 %For instance, before GPS became publicly available, route planning was based upon map-reading and asking directions of the locals.
@@
 In light of definitions given in the first section, robots have to interact with their physical environment.
-However, such definitions exclude any means of social interactions, even though \citeA{lan} asserts that socially interactive robots are significantly popular in society.
-Albeit popular, social robots, for instance a teacher robot or a guidance robot employed in an art gallery, appears to be decontextualized with regards to definitions provided in the first section.
+However, such definitions exclude any means of human interactions, even though \citeA{lan} asserts that socially interactive robots are significantly popular in society.
+%Albeit popular, social robots, for instance a teacher robot or a guidance robot employed in an art gallery, appears to be decontextualized with regards to definitions provided in the first section.
 This discrepancy brings about a major problem on the individual and societal levels.
-One example of this fact is that individuals have started to get strong advice from AI applications, a software crunching numbers faster than a man can do, rather than a close friend who might know better about the individual seeking advice, such as the taste in music or book.
+One example of this fact is that individuals have started to get strong advice from AI applications, a software crunching numbers faster than a man can do, rather than a close friend who might know better about the individual seeking advice, such as his/her taste in music or books.
 Even though this issue seems to have a minor flip-side, once it is aggregated \citeA{lan} claims, it will create true alienation from society and confusion regarding personhood. \par
-Another matter that deeply affects human psychology is that innovative superiority of robots seems to increase profitability and efficiency in workplaces, thereby undermining the true value of failures.
-Given that failures are one of most essential component of human learning process, superiority of AI tend to discourage individuals to commit any form of actions due to fear of failures. 
+Another matter that deeply affects human psychology is that innovative superiority of robots seems to increase profitability and efficiency in the workplaces, thereby undermining the true value of failures.
+Given that failures are one of most essential component of the human learning process, the superiority of AI tends to discourage individuals from committing any form of actions due to the fear of failure.
 This fear impedes the same body of individuals to learn, hindering them completely to trust human judgment .
-Depression and other similar psychological challenges are the most profound indicators of the aftermaths of inaccurate definition of AI. \par
+Depression and other similar psychological challenges are the most profound indicators of the aftermath of an inaccurate definition of AI. \par
 
-Furthermore, the rise of computers has led to lessen the human employment starting from late 70's.
-Because of the downsizing tendency of corporations which resulted from this replacement, millions of low-skilled workers lost their jobs.
+Furthermore, the rise of computers has led to the lessening the human employment starting from the late 70's.
+Because of the downsizing tendency of corporations which has resulted from this replacement, millions of low-skilled workers have lost their jobs.
 Robots and AI supposedly represent the maxima of accuracy and repeatability, which promotes reliance on AI thanks to their cognitive and learning abilities that outperform human abilities.
-Given that historic fact, \citeA{gre} predict that this reliance might cause an inevitable replacement of low-skilled laborers with the more powerful robots, akin to the aftermaths of the computerization era.
+Given that historic fact, \citeA{gre} predict that this reliance might cause an inevitable replacement of low-skilled laborers with the more powerful robots, akin to the aftermath of the computerization era.
 In light of that prediction, highly developed economies may show a strong recession due to the significant loss in human work power and if this aggressive expansion continues, other occupations and professions will be under the same risk of mechanization.
@@
 
-Along with the economical effects of workplace computerization, eradication of low-skilled jobs may lead to the expansion of the gap among the social groups \cite{gre}.
-For instance, as the first paragraph of this section indicates, those who can use computers or know how to develop software have reached to higher classes in societies, while others could not seize the same momentum.
-This computerization instructs young individual belong to lower layers of society to believe that there is no way to elevate in society.
-This expansion in the gap with in society and among the social groups clearly contradicts to the societal goals of robotics.
+Along with the economic effects of workplace computerization, eradication of low-skilled jobs may lead to the expansion of the gap among the social groups \cite{gre}.
+For instance, as the first paragraph of this section indicates, those who can use computers or know how to develop software have reached the higher classes in societies, while others could not seize the same momentum.
+This computerization instructs young individuals belonging to the lower layers of society to believe that there is no way to elevate in society.
+This expansion in the gap within society and among the social groups clearly contradicts the societal goals of robotics.
 
 \section{Conclusions}
-The notion of increasingly accelerating technology with the precious help of scientific research studies thrills individuals.
-%However, these two prominent concepts of technology closely resembles another, the Internet.
-%, otherwise yet another issue will jump into debate topics before formers could be solved.
+The notion of increasingly accelerating technology with the valuable help of scientific research studies thrills individuals.
+
 Yet, it is crucially important to decide whether or not robots are simply functional machines that are utilitarian in their responsibilities and nothing more.
-If so, it is irrelevant to discuss the ethical problems arisen by its creation because the problems will become a question of accuracy of the source code that runs robots and.
+If so, it is irrelevant to discuss the ethical problems that have arisen by its creation because the problems will become a question of accuracy of the source code that runs robots and.
 In that case, the matter should be discussed would be how to mitigate, even eradicate, human errors taking place when roboticists develop robots and AI. \par
-As for the ethical problems, there are two distinctive approaches to the future of robots.
-The first one is that robots will highly likely to be no more prone to erroneousness than any other human invention.
-If evolutionary psychology is taken into account, the first members of fully autonomous robots will also evolve rapidly toward their excellence.
+As for the ethical problems, there are two distinctive approaches to the future of robots. The first one is that robots will highly likely be no more prone to errors than any other human invention.
+If evolutionary psychology is taken into account, the first fully autonomous robots will also evolve rapidly toward their excellence.
 Moreover, the second approach claims that as the expansion and the accessibility to AI and robotics increase, the prediction of the aftermath has become obsolete due to the late response of individuals and their wisdom toward these technologies.
-Thus, robotics should be scrutinized by various roboticists, scientists, ethicists, psychologists, sociologists and many other experts to understand and formulate its limitations and endless possibilities, otherwise yet another issue will accumulate into debate topics before former ones could be solved.
-
-%\cite{Kerb}'s evaluation of the Japanese artworks concludes that robots, depicted and envisioned in the artworks, are neither overlords nor serf-laborers. 
+Thus, robotics should be thoroughly scrutinized by various roboticists, scientists, ethicists, psychologists, sociologists and many other experts to understand and formulate its limitations and endless possibilities, otherwise yet another issue will develop into controversy before former ones can be solved like in the case of Genetically Modified Organisms and the Internet.
 \bibliographystyle{apacite}

### 2015-06-16 manuscript.tex
Change Front Page Organization
Last Commit

@@
 \author{Murat Ambarkutuk}
-\affiliation{English Language Institute, University of Delaware \\ murata@udel.
-edu}
-\note{First Draft; 6/8/2015; \LaTeX}
+\affiliation{English Language Institute, University of Delaware \\ murata@udel.edu}
+\note{Manuscript, \today \\ \LaTeX}
 \usepackage{apacite}
@@
 Thus, this paper explores problems related to legal, ethical frameworks and then analyzes the numerous definitions and applications of these technologies which pose challenges on varying levels, from individual to societal.
-The formation of this paper is as follows: The first and second sections scrutinize the definitions and the applications of robots, respectively, to attribute the reasons for these issues, and the third section then categorizes the issues that robotics have brought about.
+The organization of this paper is as follows: The first and second sections scrutinize the definitions and the applications of robots, respectively, to attribute the reasons for these issues, and the third section then categorizes the issues that robotics have brought about.
 
@@
 The second definition, however, takes autonomy into account.
-A robot, \citeA{pear} quotes in his article, must have a detailed idea of any action formed by a rigorous plan, accurate reasoning and precise action to interact with its physical environment, which closely aligns with the definition provided by \cite{lin}.
+A robot, \citeA{pear} quotes in his article, must have a detailed scheme of any action formed by a rigorous plan, accurate reasoning and precise action to interact with its physical environment, which closely aligns with the definition provided by \citeauthor{lin} \citeyear{lin}.
 \citeauthor{lin} \citeyear[p.~943]{lin} define a robot as "an engineered machine that senses, thinks, and acts".
@@
 % A strip from the old paper
-In order to make its obfuscated definition clear, the tasks of AI should be addressed.
+In order to make its obscure definition clear, the tasks of AI should be addressed.
 On the one hand,  \citeA[p.~943]{lin} note that robots are employed in tasks called "three D's" referring to "dull, dirty, or dangerous" tasks.
-From that instruction, a robot should replace a human where the task contains either mundane chores, or risks of contamination, or threats to human lives.
+Based on these tasks, a robot should replace a human where the task contains either mundane chores, or risks of contamination, or threats to human lives.
 \par 
@@
 \section{The Most Profound Issues of Robotics}
-From its very early contemplations, AI has been the most controversial issue within the engineering and scientific societies due to its ethical problems.
+From its very early conception, AI has been the most controversial issue within the engineering and scientific societies.
 The near future is fecund with many dilemmas which humankind, sooner or later, will face regarding AI's moral integrity and its position in society.
@@
 % <readagain>
-This utilization of a weaponized robotic army would boost the vast possession of ammunition instead of mediating inter-governmental conflicts.
+This utilization of a weaponized robotic army would boost the vast possession of weaponry instead of mediating inter-governmental conflicts.
 % </readagain>
@@
 Moreover, hacking has been the most debated issue since the Internet became publicly available.
-Along with many other safety issues, hacking is an associated issue regarding when it comes to securely integrating robots in work settings.
+Along with many other safety issues, hacking is an associated issue regarding the secure integration of robots securely integrating robots in work settings.
 In this case, the risk is not identity theft or any other illegal activity. % since the anticipations for robots to be employed in wide variety of tasks.
@@
 \citeA{gre} examine that ambiguity by posing a controversial question: "Who will be responsible for the results of AI's actions and failures?"
-Since the contemplation of AI and robots replacing laborers in some tasks indicates that robots will supposedly make their own choices to take actions according to these choices, another interesting question arises: "Would robots be prosecuted -maybe executed- because of their failures?"
-Similar to the questions above, there are many questions that governments need to address by creating regulations and laws with which robots will comply. \par
+Since AI and robots have begun replacing laborers in some tasks, this phenomenon indicates that robots will supposedly make their own choices and take actions according to these choices.
+That controversy causes another interesting question to arise: "Would robots be prosecuted maybe executed because of their failures resulting in fatal accidents?"
+Similar to the questions above, there are many considerations that governments need to address by creating regulations and laws with which robots will comply. \par
 Furthermore, many researchers have been questioning whether or not these super-intelligent agents should have duties to society, such as paying taxes; if so, to what extent should governments  give social rights to robots?
@@
 Social interaction is what differentiates humans from machines.
-However, as the research studies toward creation of AI have gone deeper, robots have become more socially interactive with society.
+However, as the research studies toward creation of AI have gone deeper, robots have become more socially interactive.
 %For instance, before GPS became publicly available, route planning was based upon map-reading and asking directions of the locals.
@@
 %This issue truly matters due to the fact that alienation from the society relies on that misconception.
-In light of definitions given in the first section, robots have to interact with their physical environment.
+%In light of definitions given in the first section, robots have to interact with their physical environment.
+According to the definitions of robots in the first section, robots have to interact with their physical environment.
 However, such definitions exclude any means of human interactions, even though \citeA{lan} asserts that socially interactive robots are significantly popular in society.
@@
 This discrepancy brings about a major problem on the individual and societal levels.
-One example of this fact is that individuals have started to get strong advice from AI applications, a software crunching numbers faster than a man can do, rather than a close friend who might know better about the individual seeking advice, such as his/her taste in music or books.
-Even though this issue seems to have a minor flip-side, once it is aggregated \citeA{lan} claims, it will create true alienation from society and confusion regarding personhood. \par
-Another matter that deeply affects human psychology is that innovative superiority of robots seems to increase profitability and efficiency in the workplaces, thereby undermining the true value of failures.
+One example of this fact is that individuals have started to get strong assistance from AI applications, a software crunching numbers faster than a man can do, rather than a close friend who might know better about the individual seeking recommendations, such as his/her taste in music or books.
+Even though this issue seems to have minor flip-sides, once they are aggregated \citeA{lan} claims, they will create true alienation from society and confusion regarding personhood. \par
+Another matter that deeply affects human psychology is that innovative superiority of robots seems to increase profitability and efficiency in the workplace, thereby undermining the true value of failures.
 Given that failures are one of most essential component of the human learning process, the superiority of AI tends to discourage individuals from committing any form of actions due to the fear of failure.
-This fear impedes the same body of individuals to learn, hindering them completely to trust human judgment .
+This fear impedes the same body of individuals to learn, completely hindering them from trusting human judgment.
 Depression and other similar psychological challenges are the most profound indicators of the aftermath of an inaccurate definition of AI. \par
 
-Furthermore, the rise of computers has led to the lessening the human employment starting from the late 70's.
+Furthermore, the rise of computers has led to the lessening of human employment starting from the late 70's.
 Because of the downsizing tendency of corporations which has resulted from this replacement, millions of low-skilled workers have lost their jobs.
-Robots and AI supposedly represent the maxima of accuracy and repeatability, which promotes reliance on AI thanks to their cognitive and learning abilities that outperform human abilities.
+Robots and AI supposedly represent the maxima of accuracy and repeatability, which promotes reliance on AI, thanks to their cognitive and learning abilities that outperform human abilities.
 Given that historic fact, \citeA{gre} predict that this reliance might cause an inevitable replacement of low-skilled laborers with the more powerful robots, akin to the aftermath of the computerization era.
@@
 Yet, it is crucially important to decide whether or not robots are simply functional machines that are utilitarian in their responsibilities and nothing more.
-If so, it is irrelevant to discuss the ethical problems that have arisen by its creation because the problems will become a question of accuracy of the source code that runs robots and.
-In that case, the matter should be discussed would be how to mitigate, even eradicate, human errors taking place when roboticists develop robots and AI. \par
-As for the ethical problems, there are two distinctive approaches to the future of robots. The first one is that robots will highly likely be no more prone to errors than any other human invention.
+If so, it is irrelevant to discuss the ethical problems that have arisen by its creation because the problems will become a question of accuracy of the source code that runs robots.
+In that case, the matter that should be discussed would be how to mitigate, even eradicate, human errors taking place when roboticists develop robots and AI. \par
+As for the problems, there are two distinctive approaches to the future of robots. The first one is that robots will highly likely be no more prone to errors than any other human invention.
 If evolutionary psychology is taken into account, the first fully autonomous robots will also evolve rapidly toward their excellence.
 Moreover, the second approach claims that as the expansion and the accessibility to AI and robotics increase, the prediction of the aftermath has become obsolete due to the late response of individuals and their wisdom toward these technologies.
-Thus, robotics should be thoroughly scrutinized by various roboticists, scientists, ethicists, psychologists, sociologists and many other experts to understand and formulate its limitations and endless possibilities, otherwise yet another issue will develop into controversy before former ones can be solved like in the case of Genetically Modified Organisms and the Internet.
+Thus, robotics should be thoroughly scrutinized by various roboticists, scientists, ethicists, psychologists, sociologists and many other experts to understand and formulate its limitations and endless possibilities.
+Otherwise, yet another issue will develop into controversy before former ones can be solved like in the case of genetically modified organisms and the Internet.
 \bibliographystyle{apacite}
